---
title: "Data Exploration"
output: html_document
date: "2024-09-16"
---

# Description of Overall Coding File

This file details the process of preparation of the combined dataset for Asthma and COPD-related factors. 

Environmental data is also called from weather.gov.sg using API. Environmental data was collated from multiple weather stations in Singapore, and aggregated to obtain the respective measures.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(stringr)
library(MASS)
library(readxl)
library(httr)
library(jsonlite)
library(lubridate)
library(tidyr)
library(ISOweek)
library(zoo)
```

## Loading Dataframes

We first load the original data alongside the introduction to the conversion of week columns to epiweek. Apart from that, we also prepared the custom aggregate function to prepare the weather data (API-called).

```{r}
copd_df = read_excel("COPD_admissions_2012_2023.xlsx")
asthma_df = read_excel("Asthma_admissions_2012_2023.xlsx")

# Function to compute epiweek
compute_epiweek = function(year, month, day) {
  date = as.Date(sprintf("%04d-%02d-%02d", year, month, day))
  start_of_year = as.Date(sprintf("%04d-01-01", year))
  day_diff = as.numeric(difftime(date, start_of_year, units = "days"))
  week_number = floor(day_diff / 7) + 1
  if (week_number == 53){
    week_num_new = 52
    return(week_num_new)
  }
  return(week_number)
}

# Function to convert YYYYWW to Week object
convert_to_epiweek = function(yyyww) {
  year = as.integer(substr(yyyww, 1, 4))
  week = as.integer(substr(yyyww, 5, 6))
  iso_week_str = sprintf("%d%02d", year, week)
  return(iso_week_str)
}

# Aggregation function for Weather Data
custom_agg = function(column, col_name) {
  if (grepl("Max|Maximum|Highest", col_name)) {
    return(max(column, na.rm = TRUE))
  } else if (grepl("Min|Minimum", col_name)) {
    filtered_column = column[column > 0]
    return(min(filtered_column, na.rm = TRUE))
  } else {
    return(mean(column, na.rm = TRUE))
  }
}
```

## Calling of API to get data from weather.gov.sg

Calling of API to get environmental data - it is to note that on particular days some weather stations may not record the data too!

```{r}
# res = GET('https://www.weather.gov.sg/files/dailydata/DAILYDATA_S06_201904.csv')
# status_code(res)
# writeBin(content(res, "raw"), "dailydata.csv")
# final_df <- read_csv("dailydata.csv", locale = locale(encoding = "ISO-8859-1"))
# final_df <- final_df %>%
#   mutate(across(everything(), as.character)) %>%
#   mutate(across(everything(), ~na_if(.x, "—"))) %>%
#   mutate(across(everything(), ~na_if(.x, "\x97")))%>%
#   mutate(across(everything(), ~na_if(.x, "\u0097")))

generate_csv = function(url) {
  response = GET(url)
  if (status_code(response) == 200) {
    writeBin(content(response, "raw"), "dailydata.csv")
    final_df = read_csv("dailydata.csv", locale = locale(encoding = "ISO-8859-1"))
    final_df = final_df %>%
      mutate(across(everything(), as.character)) %>%
      mutate(across(everything(), ~na_if(.x, "—"))) %>%
      mutate(across(everything(), ~na_if(.x, "\x97"))) %>%
      mutate(across(everything(), ~na_if(.x, "\u0097")))
    
    return(final_df)
  } else {
    return(NULL)
  }
}

# Define column names (assuming the first call to generate_csv retrieves the columns)
final_df = generate_csv('https://www.weather.gov.sg/files/dailydata/DAILYDATA_S50_201508.csv')
col_names = names(final_df)

# Loop to construct URLs and collect data
for (i in 1:130) {
  if (i < 10) {
    country_code = paste0("S0", i)
  } else {
    country_code = paste0("S", i)
  }
  
  for (year in 2012:2023) {
    for (month in 1:12) {
      year_month = sprintf("%04d%02d", year, month)
      url = paste0('https://www.weather.gov.sg/files/dailydata/DAILYDATA_', country_code, '_', year_month, '.csv')
      url_csv = generate_csv(url)
      
      if (!is.null(url_csv)) {
        # Ensure columns match
        colnames(url_csv) = col_names
        final_df = rbind(final_df, url_csv)
      }
    }
  }
}

```

## Cleaning of Environmental Dataset

Performance of the following functions
- Computation of Epiweek Function
- Aggregation of Environmental Variables
- Generation of heat-related variables (weeks containing days of EXTREME heat, and heat-wave weeks)

```{r pressure, echo=FALSE}
# Read the CSV file
df_original = read.csv("r_called_env_variables.csv")

# Cleaning of environmental data
env_data_cleaning = function(df) {
  
  df = df %>%
    distinct() %>%
    drop_na(Year, Month, Day) %>%
    mutate(across(c(Year, Month, Day), as.integer)) %>%
    dplyr::select(-Station) %>%
    mutate(across(everything(), ~ as.numeric(.)))
  
  # Apply epiweek calculation
  df = df %>%
    rowwise() %>%
    mutate(EpiWeek = compute_epiweek(Year, Month, Day)) %>%
    ungroup() %>%
    mutate(EpiWeek_str = sprintf("%02d", EpiWeek),
           year_str = sprintf("%02d", Year),
           epiweek_str = paste0(year_str, EpiWeek_str),
           epiweek = convert_to_epiweek(epiweek_str)) %>%
    dplyr::select(-epiweek_str, -EpiWeek_str, -year_str, -EpiWeek, -Year, -Day, -Month)
  
  # Aggregation function to compute functions
  env_variables = df %>%
     group_by(epiweek) %>%
     summarise(across(everything(), ~ custom_agg(., cur_column()), .names = "{col}")) %>%
     column_to_rownames(var = "epiweek") %>%
     dplyr::select(-c(2,3,4))
    
  colnames(env_variables) = c("Daily Total Rainfall (mm)", "MeanTemp (C)", "MaxTemp (C)", "MinTemp (C)", "MeanWind (kmh)", "MaxWind (kmh)")
  return(env_variables)
}
colnames(df_original)

heat_variables = function(df) {
  df_rolling = df %>%
    distinct() %>%
    drop_na(Year, Month, Day) %>%
    mutate(across(c(Year, Month, Day), as.integer)) %>%
    dplyr::select(-Station) %>%
    mutate(across(everything(), ~ as.numeric(.))) %>%
    dplyr::select(Year, Month, Day, "Maximum.Temperature...C.", "Mean.Temperature...C.") %>%
    drop_na("Maximum.Temperature...C.", "Mean.Temperature...C.") %>%
    ungroup() %>%
    group_by(Year,Month,Day) %>%
    rename("MaxTemp" = "Maximum.Temperature...C.",
           "MeanTemp" = "Mean.Temperature...C.") %>%
    summarise(MaxTemp = max(MaxTemp,na.rm=T),
           MeanTemp = mean(MeanTemp,na.rm=T),
           .groups = "drop") %>%
    mutate(very_hot_day = ifelse(MaxTemp > 33, 1, 0),
           AvgMaxTemp = rollapply(MaxTemp, width = 3, FUN = mean, align = "right", fill = NA),
           AvgMeanTemp = rollapply(MeanTemp, width = 3, FUN = mean, align = "right", fill = NA)) %>%
    mutate(heat_wave = ifelse(AvgMaxTemp >= 35 & AvgMeanTemp >= 29, 1, 0))
  
  # Apply epiweek calculation
  df_int = df_rolling %>%
    rowwise() %>%
    mutate(EpiWeek = compute_epiweek(Year, Month, Day)) %>%
    ungroup() %>%
    mutate(EpiWeek_str = sprintf("%02d", EpiWeek),
           year_str = sprintf("%02d", Year),
           epiweek_str = paste0(year_str, EpiWeek_str),
           epiweek = convert_to_epiweek(epiweek_str)) %>%
    dplyr::select(-epiweek_str, -EpiWeek_str, -year_str, -EpiWeek, -Year, -Day, -Month) %>%
    ungroup() %>%
    group_by(epiweek) %>%
    summarise(hot_week = sum(very_hot_day,na.rm=T),
           heat_wave = sum(heat_wave,na.rm=T),
           hot_week_indicator = ifelse(hot_week > 0, 1, 0),
           heat_wave_week = ifelse(heat_wave > 0, 1, 0)) %>%
    dplyr::select(-c(hot_week, heat_wave))
  env_variables = df_int %>% column_to_rownames(var = "epiweek")
  return(env_variables)
}
env_variables = env_data_cleaning(df_original)
additional_variables = heat_variables(df_original)
merged_df = merge(env_variables, additional_variables, by = "row.names")
rownames(merged_df) = merged_df$Row.names
merged_df = merged_df %>% dplyr::select(-Row.names)
# Save to CSV if needed
write.csv(merged_df, "env_variables_clean_220924.csv")


```

# Cleaning of COPD and Asthma Dataframes, and merging of dataframes with environmental variables
- Renaming of COPD and Asthma Dataframes to ensure no overlap in columns
- Merging of COPD, Asthma, Environment Dataframe to form a combined dataframe
- Conversion of raw discharges to that of 7 days (for final week of each year). This is because some weeks have more than 7 days given that the data procurers considered 1 January as the first day of the first week in the year (hence final week of the years may not have 7 days).

```{r}
# colnames(asthma_df)
# asthma_df[1,]
colnames_copd = c("year","week","admissions","residents","overall_rate",
                  "age_40_to_54_admissions","age_55_to_64_admissions","age_65_to_74_admissions",
                  "age_75_to_84_admissions","age_85_above_admissions", "female_admissions","male_admissions",
                  "age_40_to_54_residents","age_55_to_64_residents","age_65_to_74_residents",
                  "age_75_to_84_residents","age_85_above_residents","female_residents","male_residents",
                  "age_40_to_54_overall_rate","age_55_to_64_overall_rate","age_65_to_74_overall_rate",
                  "age_75_to_84_overall_rate","age_85_above_overall_rate","female_overall_rate","male_overall_rate")
colnames_asthma = c("year","week","admissions","residents","overall_rate",
                    "age_0_to_14_admissions","age_15_to_39_admissions",
                    "age_40_to_54_admissions","age_55_to_64_admissions","age_65_to_74_admissions",
                    "age_75_to_84_admissions","age_85_above_admissions", "female_admissions","male_admissions",
                    "age_0_to_14_residents","age_15_to_39_residents",
                    "age_40_to_54_residents","age_55_to_64_residents","age_65_to_74_residents",
                    "age_75_to_84_residents","age_85_above_residents","female_residents","male_residents",
                    "age_0_to_14_overall_rate","age_15_to_39_overall_rate",
                    "age_40_to_54_overall_rate","age_55_to_64_overall_rate","age_65_to_74_overall_rate",
                    "age_75_to_84_overall_rate","age_85_above_overall_rate",
                    "female_overall_rate","male_overall_rate")
colnames(copd_df) = colnames_copd
colnames(asthma_df) = colnames_asthma
copd_df_1 = copd_df[2:nrow(copd_df),]
asthma_df_1 = asthma_df[2:nrow(asthma_df),]

data_cleaning = function(df,df_type) {
  rename_columns = function(col, name) {
    if (!(name %in% col) && col != "epiweek") {
      return(paste0(col, "_", name))
    }
    return(col)
  }
  # Create week and year strings
  df = df %>%
    mutate(
      week_str = sprintf("%02d", week),
      year_str = sprintf("%02d", year),
      epiweek_str = paste0(year_str, week_str),
      epiweek = sapply(epiweek_str, convert_to_epiweek)
    ) %>%
    # Drop unnecessary columns
    dplyr::select(-epiweek_str, -week_str, -year_str, week, year) %>%
    # Move epiweek to the first column and set it as the row name
    relocate(epiweek) %>%
    column_to_rownames(var = "epiweek") %>% 
    rename_with(~ sapply(., rename_columns, df_type), .cols = everything())
  
  return(df)
}

final_week_days = function(year){
  start = paste0('01/01/',as.character(year))
  start = as.Date(start,format = '%m/%d/%Y')
  end = paste0('12/31/',as.character(year))
  end = as.Date(end,format = '%m/%d/%Y')
  days = end-start
  final_week = (as.numeric(days)+1)-51*7
  return(final_week)
}

# Counting the number of days within each week (for renormalisation)
days_df = function(start_year,end_year){
  overall = data.frame(matrix(nrow=0,ncol=2))
  colnames(overall) = c("week","num_days")
  for (year in start_year:end_year){
    for (week in 1:52){
      if (week < 10){
        week_str = paste0("0",as.character(week))
      } else {
        week_str = as.character(week)
      }
      time = paste0(as.character(year),week_str)
      if (week == 52){
        to_add = data.frame(week = time, num_days = final_week_days(year))
      } else {
        to_add = data.frame(week = time, num_days = 7)
      }
      overall = rbind(overall,to_add)
    }
  }
  return(overall)
}

days = days_df(2012,2023)

copd_clean = data_cleaning(copd_df_1,"COPD")
asthma_clean = data_cleaning(asthma_df_1,"asthma")

copd_clean$rownames = rownames(copd_clean)
asthma_clean$rownames = rownames(asthma_clean)
env_dataset = read.csv("env_variables_clean_220924.csv") %>% rename("rownames" = "X") %>% mutate(rownames=as.character(rownames))
colnames(env_dataset) = c("rownames","Daily_Total_Rainfall","MeanTemp","MaxTemp","MinTemp","MeanWind","MaxWind","hot_week_indicator","heat_wave_week")

combined_df = copd_clean %>% 
  left_join(asthma_clean, by = c("rownames","year_COPD" = "year_asthma","week_COPD" = "week_asthma")) %>% 
  left_join(env_dataset,by="rownames") %>% 
  left_join(days, by=c("rownames" = "week")) %>% 
  column_to_rownames(var = "rownames") %>%
  rename("year" = "year_COPD",
         "week" = "week_COPD")

combined_df_edited = combined_df %>%
  # dplyr::select(-matches("overall_rate")) %>%
  mutate(across(contains("admissions"), ~ ceiling((. / num_days) * 7))) %>%
  dplyr::select(-num_days) %>%
  rename("cases_copd" = "admissions_COPD",
         "cases_asthma" = "admissions_asthma") %>%
  rename_with(~ gsub("_COPD", "_copd", .), contains("_COPD")) %>%
  rename_with(~ gsub("_admissions", "", .), contains("_admissions"))
  
# Saving final dataframe
write.csv(combined_df_edited,"combined_asthma_env_080225_norates.csv")
```
