---
title: "Data Exploration"
output: html_document
date: "2024-09-16"
---

In this EDA file, the following actions were performed:

(1) Generation of Summary Statistics for the variables in the dataset.

(2) Generation of PACF and Time Series plots for each disease is done to obtain the optimum lag, while also identifying the structural break within the dataset.

(3) Determination of the need of the consideration of nonlinear relationships between covariates and outcome variables.

Libraries used in this file are loaded
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(stringr)
library(MASS)
library(readxl)
library(httr)
library(jsonlite)
library(lubridate)
library(tidyr)
library(ISOweek)
library(ggplot2)
library(viridis)
library(tseries)
library(cowplot)

combined_df = read_csv("combined_asthma_env_080225_norates.csv")%>%
  column_to_rownames(var = "...1")

zero_proportions <- combined_df %>%
  summarise(across(contains("admissions"), ~ mean(. == 0, na.rm = TRUE)))

cols_to_remove = names(zero_proportions)[zero_proportions > 0.5] # COPD 40 to 54, asthma 0 to 14

# Keep only relevant columns in the dataset
combined_df = combined_df %>%
  dplyr::select(-c(cols_to_remove,age_40_to_54_residents_COPD,age_40_to_54_overall_rate_COPD,age_0_to_14_residents_asthma,age_0_to_14_overall_rate_asthma))
```

# Action 1: Summary Statistics

The following describes the summary statistics of the dataset:

```{r}
summary_stats = function(data) {
  data.frame(
    Max = round(sapply(data, max, na.rm = T), 2),
    Mean = round(sapply(data, mean, na.rm = T), 2),
    Min = round(sapply(data, min, na.rm = T), 2),
    Variance = round(sapply(data, var, na.rm = T), 2)
  )
}

summary_df = summary_stats(combined_df)
summary_df
```

# Action 2: Generation of PACF plots

Firstly, stationarity of the dataframes for COPD and Asthma is checked using the ADF test. From the results, the outcome variable is stationary using ADF.
```{r}
rownames_split = as.numeric(rownames(combined_df_edited))
# Extraction of Years and Months
years = floor(rownames_split / 100) 
weeks = rownames_split %% 100  

start_year = years[1]
start_week = weeks[1]

ts_data = ts(combined_df_edited$cases_copd, start = c(start_year, start_week), frequency = 52)
ts_data_asthma = ts(combined_df_edited$cases_asthma, start = c(start_year, start_week), frequency = 52)

adf.test(ts_data)$p.value
adf.test(ts_data_asthma)$p.value
```

## Plotting of PACF diagram to find optimum lag for pure Autoregressive Model
Next, using Ljung-Box test, the optimum lag (Lag = 1) is determined for each model using the initial training set (50% of the dataset size)
```{r pressure, echo=FALSE}
pacf_plotter = function(df, var){
  pacf_values = acf(df[[var]], type = "partial", plot = FALSE)
  pacf_df = data.frame(
    Lag = as.vector(pacf_values$lag),
    PACF = as.vector(pacf_values$acf)
  )
  
  rownames_split = as.numeric(rownames(df))
  years = floor(rownames_split / 100) 
  weeks = rownames_split %% 100  
  
  start_year = years[1]
  start_week = weeks[1]
  
  ts_data = ts(df[[var]], start = c(start_year, start_week), frequency = 52)
  lag_val = 0
  for (lag_num in 1:20){
    lag_val = lag_val + 1
    pstat = Box.test(residuals(arima(ts_data,order=c(lag_num,0,0))), lag = 3, type = "Ljung-Box")$p.value
    # return(pstat)
    if (pstat > 0.01){
      final_pvalue = pstat
      break
    } else {
      next
    }
  }
  
  pacf_df = pacf_df %>% mutate(Shades = ifelse(Lag <= lag_val, "Used Lag", "Unused Lag"))
  
  final_plot = ggplot(pacf_df, aes(x = Lag, y = PACF, fill = Shades)) +
    geom_bar(stat = "identity") +
    labs(x = "Lags",
         y = "Partial Autocorrelation") +
    scale_y_continuous(limits=c(-0.1,0.5)) +
    theme_minimal() +
    theme(
      axis.ticks = element_line(),  # Add axis ticks
      axis.ticks.length = unit(1, "cm"),
      plot.title = element_text(hjust = 0.5, size = 30),
      legend.position = c(0.65, 1),  # Top-left corner
      legend.justification = c(0, 1),
      panel.grid = element_blank(),
      # panel.background = element_rect(fill = "lightblue"),
      legend.box.background = element_rect(color = "black", fill = "white", size = 0.5),
      # legend.background = element_rect(fill = "white", color = NA),
      axis.title.y = element_text(face = "bold", size = 50),
      axis.title.x = element_text(face = "bold", size = 50),
      panel.border = element_rect(color = "black", fill = NA, size = 1),
      strip.text = element_text(size = 50),
      axis.text = element_text(size = 50),
      legend.title = element_text(face = "bold", size=50),
      legend.text = element_text(size=50)
    )
  return(final_plot)
}

new_combined = combined_df_edited[1:floor(0.5*nrow(combined_df_edited)),]

copd_plot = pacf_plotter(new_combined, "cases_copd") + theme(legend.position = "none")+
  scale_y_continuous(breaks = waiver(),limits=c(-0.1,0.5)) + 
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  labs(x = NULL)

legend = get_legend(
    pacf_plotter(new_combined, "cases_copd") +
      theme(legend.position = "right",
            legend.justification = c(0.3, 0.5),
            legend.box.margin = margin(0, 0, 0, -2),
            legend.title = element_text(size = 50, face = "bold"),
            legend.text = element_text(size = 45))
  )

asthma_plot = pacf_plotter(new_combined, "cases_asthma")+ theme(legend.position = "none")

overall = plot_grid(plot_grid(copd_plot, asthma_plot,labels = "AUTO", ncol = 1, label_size = 70,hjust = 0.05,vjust=1),
                            legend,
                            ncol = 2, # 2 columns: one for plots, one for the legend
                            rel_widths = c(6, 1)) # Adjust widths (6:1 for better spacing)

ggsave(file="combined_pacf_080225.pdf", plot=overall, width=30, height=22.5, limitsize=FALSE)
```

# Action 3: Determination of the need to consider nonlinear relationships

The decision of smoothing of disease and environmental Factors is made based on AIC values generated from GAMs.

First, variables are lagged (based on the optimum lag), and generation of a 1-month ahead forecast dataset was used.

```{r}
# colnames(combined_df_edited)
copd_discharge_significant_predictors = c("female_asthma", "male_asthma", "cases_asthma", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall","age_15_to_39_asthma", "age_40_to_54_asthma","age_55_to_64_asthma","age_65_to_74_asthma", "age_75_to_84_asthma","age_85_above_asthma")

asthma_discharge_significant_predictors = c("female_copd", "male_copd", "age_55_to_64_copd", "age_65_to_74_copd", "age_75_to_84_copd","age_85_above_copd", "cases_copd", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")

data_editing = function(df_filename, outcome, significant_predictors){
  combined_df = read_csv(df_filename)%>%
  column_to_rownames(var = "...1")
  colnames(combined_df) = gsub(" \\(C\\)", "", colnames(combined_df))
  colnames(combined_df) = gsub(" \\(mm\\)", "", colnames(combined_df))
  colnames(combined_df) = gsub(" \\(kmh\\)", "", colnames(combined_df))
  colnames(combined_df) = gsub(" ", "_", colnames(combined_df))
  
  if (str_detect(outcome, "copd")){
    popn = "residents_copd"
  } else if (str_detect(outcome,"asthma")){
    popn = "residents_asthma"
  }
  new_combined = combined_df %>% 
    dplyr::select(year, week, outcome, popn, significant_predictors)
  return(new_combined)
}

generate_lagged_df = function(df, copd_lag_num, asthma_lag, env_lag, outcome){
  lagged_df = df
  lagged_cols_df = lagged_df %>%
      dplyr::select(outcome) 
  
  # Customisation of function based off the outcome (COPD / Asthma)
  if (str_detect(outcome, "copd")){
    disease_popn = "residents_copd"
    other_disease = "asthma"
    outcome_lag = copd_lag_num
    other_disease_lag = asthma_lag
  } else if (str_detect(outcome, "asthma")){
    disease_popn = "residents_asthma"
    other_disease = "copd"
    outcome_lag = asthma_lag
    other_disease_lag = copd_lag_num
  }
  
  # Loop through all columns in the dataset
  for (col in colnames(df)){
    if (col == "year"|col == "week"){
      next
    } else if (col == disease_popn){
      lagged_col = dplyr::lag(df[[col]], 1)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", 1) := (lagged_col))
      } else if (col == outcome){
      for (i in 1:outcome_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := (lagged_col))
      }
    } else if (grepl(other_disease, col)){
      for (i in 1:other_disease_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := (lagged_col))
      }
    } else {
      for (i in 1:env_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := lagged_col)
      }
    }
  }
  lagged_df_final = na.omit(lagged_cols_df)
  return(lagged_df_final)
}

create_stepped_dataset = function(df, horizon, outcome) {
  shifted_df = df
  y = dplyr::lead(shifted_df[[outcome]], n = (horizon - 1))
  
  if (horizon != 1) {
    X = shifted_df[1:(nrow(shifted_df)-(horizon-1)),] # Removing the number of rows that y was shifted up
  } else {
    X = shifted_df
  }
  X = X %>% dplyr::select(-outcome) # Removing of outcome variable
  y = na.omit(y)
  
  return(list(X = X, y = y))
}

generate_gam_df = function(df_link, outcome_var, copd_lag_num = 3, asthma_lag = 3, env_lag = 1, horizon, significant_predictors, training_limit = 0.5){
  df = data_editing(df_link, outcome_var, significant_predictors = significant_predictors)
  env_variables_to_lag = c("MaxWind", "MeanWind", "MaxTemp", "MinTemp", "MeanTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
  other_disease_var = setdiff(significant_predictors, 
                             c(outcome_var, env_variables_to_lag))
  if (str_detect(outcome_var,"copd")){
    disease_popn = "residents_copd"
    lagged_disease_popn = "residents_copd_L1"
    initial_theta = 10
  } else if (str_detect(outcome_var,"asthma")){
    disease_popn = "residents_asthma"
    lagged_disease_popn = "residents_asthma_L1"
    initial_theta = 10
  }
  filtered_df = df %>% 
    dplyr::select(year,week,outcome_var,disease_popn, all_of(significant_predictors))
  regression_model = generate_lagged_df(filtered_df, copd_lag_num, asthma_lag, env_lag, outcome = outcome_var)
  training_length = floor(nrow(df)*training_limit)
  X_1 = create_stepped_dataset(regression_model, horizon, outcome = outcome_var)[[1]]
  outcome_var_vec = create_stepped_dataset(regression_model, horizon, outcome = outcome_var)[[2]]
  stepped_df = cbind(X_1, outcome_var_vec) # Combination to form stepped df
  stepped_df = stepped_df %>% rename(!!outcome_var := "outcome_var_vec")
  n = nrow(stepped_df)
  stepped_df = stepped_df %>%
    mutate(across(everything(), ~ ifelse(is.infinite(.) & . < 0, 0, .)))
  stepped_df = stepped_df[1:training_length, ]
  return(stepped_df)
}

```

# Step 2: Checking whether linearly related lagged variables or non-linearly related lagged variables are better
```{r}
other_disease_var_copd = c("Female_asthma", "Male_asthma", "cases_asthma", "age_15_to_39_asthma", "age_40_to_54_asthma","age_55_to_64_asthma","age_65_to_74_asthma", "age_75_to_84_asthma")
other_disease_var_asthma = c("Female_copd", "Male_copd", "age_55_to_64_copd", "age_65_to_74_copd", "age_75_to_84_copd","age_85_above_copd", "cases_copd")
env_factors = c("Daily_Total_Rainfall","MaxTemp","MeanTemp","MinTemp","MeanWind","MaxWind")

aic_comparator = function(df_link, outcome_var, horizon, other_disease_factors, env_factors, significant_factors){
  if (str_detect(outcome_var,"copd")){
    lagged_disease_popn = "residents_copd_L1"
  } else if (str_detect(outcome_var,"asthma")){
    lagged_disease_popn = "residents_asthma_L1"
  }
  
  otherdis_lagged_factors_ns = paste(unlist(sapply(other_disease_factors, function(factor) {
                              paste0(factor, "_L", 1:3)
                              })), collapse = " + ")
  otherdis_lagged_factors_s = paste(unlist(sapply(other_disease_factors, function(factor) {
                            paste0("s(",factor, "_L", 1:3,")")
                            })), collapse = " + ")
  autoreg_lagged = paste(unlist(sapply(autoreg_factors, function(factor) {
                                paste0(factor, "_L", 1:3)
                                })), collapse = " + ")
  autoreg_lagged_s = paste(unlist(sapply(autoreg_factors, function(factor) {
                                    paste0("s(",factor, "_L", 1:3,")")
                                  })), collapse = " + ")
  env_lagged = paste(unlist(sapply(env_factors, function(factor) {
                      paste0(factor, "_L", 1:1)
                      })), collapse = " + ")
  env_lagged_s = paste(unlist(sapply(env_factors, function(factor) {
                        paste0("s(",factor, "_L", 1:1,")")
                      })), collapse = " + ")
  
  x = generate_gam_df(df_link,outcome_var,horizon = horizon,significant_predictors = significant_factors)
  
  gam_model_autoreg = bam(as.formula(paste(outcome_var, "~ offset(log(", lagged_disease_popn, ")) + ",autoreg_lagged)),
                     family = nb(link = "log"), data = x)

  gam_model_autoreg_s = bam(as.formula(paste(outcome_var, "~ offset(log(", lagged_disease_popn, ")) + ",autoreg_lagged_s)),
                       family = nb(link = "log"), data = x)
  
  gam_model_otherdis = bam(as.formula(paste(outcome_var, "~ offset(log(", lagged_disease_popn, ")) + ",otherdis_lagged_factors_ns)), family = nb(link = "log"), data = x)
  
  gam_model_otherdis_s = bam(as.formula(paste(outcome_var, "~ offset(log(", lagged_disease_popn, ")) + ",otherdis_lagged_factors_s)),
                       family = nb(link = "log"), data = x)
  
  
  gam_model_env = bam(as.formula(paste(outcome_var, "~ offset(log(", lagged_disease_popn, ")) + ",env_lagged)),
                       family = nb(link = "log"), data = x)
  
  
  gam_model_env_s = bam(as.formula(paste(outcome_var, "~ offset(log(", lagged_disease_popn, ")) + ",env_lagged_s)),
                       family = nb(link = "log"), data = x)
  
  model_names = c("gam_model_autoreg", "gam_model_autoreg_s", "gam_model_otherdis", "gam_model_otherdis_s", "gam_model_env", "gam_model_env_s")
  combined_gam = c(AIC(gam_model_autoreg), AIC(gam_model_autoreg_s), AIC(gam_model_otherdis), AIC(gam_model_otherdis_s), AIC(gam_model_env), AIC(gam_model_env_s))
  
  final_df = data.frame(horizon = horizon, model_name = model_names, aic = combined_gam)
  return(final_df)
}

copd_combined_aic_df = as.data.frame(matrix(nrow=0,ncol=3))
colnames(copd_combined_aic_df) = c("horizon", "model_name", "aic")
for (horizon_num in 1:12){
  to_add = aic_comparator("combined_asthma_env_250924.csv", outcome_var = "cases_copd", horizon = horizon_num, other_disease_factors = other_disease_var_copd, env_factors = env_factors, significant_factors = copd_discharge_significant_predictors)
  copd_combined_aic_df = rbind(copd_combined_aic_df, to_add)
}

asthma_combined_aic_df = as.data.frame(matrix(nrow=0,ncol=3))
colnames(asthma_combined_aic_df) = c("horizon", "model_name", "aic")
for (horizon_num in 1:12){
  to_add = aic_comparator("combined_asthma_env_250924.csv", outcome_var = "cases_asthma", horizon = horizon_num, other_disease_factors = other_disease_var_asthma, env_factors = env_factors, significant_factors = asthma_discharge_significant_predictors)
  asthma_combined_aic_df = rbind(asthma_combined_aic_df, to_add)
}
```