---
title: "03b models (subgroups)"
output: html_document
date: "2025-02-09"
---

In this file, we focus on the analysis of the subgroup admission rates for COPD and asthma patients. 

The following steps were performed:
(1) Generation of the following functions to better facilitate forecast generation
- Cleaning of dataframe (remove irrelevant columns since only overall subgroup admission rates are used for analysis)
- Lagged dataframe (lagged covariates) 
- Stepped dataframe with the corresponding h-step ahead forecast (for given horizon h)

(2) Main Function for models
- AR (Pure) --> only lagged outcome variables as covariates
- AR (Other Disease) --> only lagged outcome and lagged (other) disease variables as covariates
- AR (Env) --> only lagged outcome and lagged environmental variables as covariates
- AR (Mixed) --> lagged outcome, lagged (other) disease, and lagged environmental variables as covariates
- GAMLSS
- GLM-GAMSEL
- GAM-XGBoost
- MLP

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())

packages = c("tidyverse", "stringr", "MASS", "readxl", "httr", "jsonlite", 
              "lubridate", "tidyr", "ISOweek", "ggplot2", "viridis", "mgcv", 
              "tseries", "glmnet", "randomForest", "grf", "gamlss", "doParallel", 
              "foreach", "xgboost", "automl", "gamsel", "h2o")

# Function to check, install if needed, and load libraries
install_and_load = function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}

# Apply function to all packages
sapply(packages, install_and_load)

# CHANGE WORKING DIRECTORY TO WHERE YOU SAVED THE FILE
setwd("DIRECTORY")

combined_df = read_csv("combined_asthma_env_080225_norates.csv")

copd_discharge_significant_predictors = c("cases_asthma", "female_overall_rate_asthma", "male_overall_rate_asthma", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall","age_15_to_39_overall_rate_asthma", "age_40_to_54_overall_rate_asthma", "age_55_to_64_overall_rate_asthma", "age_65_to_74_overall_rate_asthma", "age_75_to_84_overall_rate_asthma", "age_85_above_overall_rate_asthma")

asthma_discharge_significant_predictors = c("cases_copd", "female_overall_rate_copd", "male_overall_rate_copd", "age_55_to_64_overall_rate_copd", "age_65_to_74_overall_rate_copd", "age_75_to_84_overall_rate_copd","age_85_above_overall_rate_copd", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")

```

# Step 1: Generation of Relevant Functions
Introduction to functions involved in the forecast generation:
- Cleaning of dataframe (remove irrelevant columns since only overall subgroup admission rates are used for analysis)
- Lagged dataframe (lagged covariates) 
- Stepped dataframe with the corresponding h-step ahead forecast (for given horizon h)

```{r}
data_editing_subgroups = function(df_filename, outcome, significant_predictors){
  combined_df = read_csv(df_filename)%>%
    column_to_rownames(var = "...1")
  actual_outcome = sub("_([^_]+)$", "", outcome)
  last_part = sub(".*_(.*)$", "\\1", outcome)
  overall_rate = colnames(combined_df)[str_detect(colnames(combined_df), paste0(actual_outcome,"_overall_rate","_",last_part))]
  new_combined = combined_df %>% 
    dplyr::select(year, week, overall_rate, significant_predictors)
  return(new_combined)
}

new_combined_copd = data_editing_subgroups("combined_asthma_env_080225_norates.csv", outcome = "male_copd", significant_predictors = copd_discharge_significant_predictors)
new_combined_asthma = data_editing_subgroups("combined_asthma_env_080225_norates.csv", outcome = "age_85_above_asthma", significant_predictors = asthma_discharge_significant_predictors)

generate_lagged_df_subgroups = function(df, copd_lag_num, asthma_lag, env_lag, outcome){
  lagged_df = df
  lagged_cols_df = lagged_df %>%
      dplyr::select(outcome) 
  
  # Customisation of function based off the outcome (COPD / Asthma)
  if (str_detect(outcome, "copd")){
    other_disease = "asthma"
    outcome_lag = copd_lag_num
    other_disease_lag = asthma_lag
  } else if (str_detect(outcome, "asthma")){
    other_disease = "copd"
    outcome_lag = asthma_lag
    other_disease_lag = copd_lag_num
  }
  
  # Loop through all columns in the dataset
  for (col in colnames(df)){
    if (col == "year"|col == "week"){
      next
    } else if (col == outcome){
      for (i in 1:outcome_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := (lagged_col))
      }
    } else if (grepl(other_disease, col)){
      for (i in 1:other_disease_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := (lagged_col))
      }
    } else {
      for (i in 1:env_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := lagged_col)
      }
    }
  }
  lagged_df_final = na.omit(lagged_cols_df)
  return(lagged_df_final)
}

create_stepped_dataset = function(df, horizon, outcome) {
  shifted_df = df
  y = dplyr::lead(shifted_df[[outcome]], n = (horizon - 1))
  
  if (horizon != 1) {
    X = shifted_df[1:(nrow(shifted_df)-(horizon-1)),] # Removing the number of rows that y was shifted up
  } else {
    X = shifted_df
  }
  X = X %>% dplyr::select(-outcome) # Removing of outcome variable
  y = na.omit(y)
  
  return(list(X = X, y = y))
}

```

# Step 2: Main Function for models

The function for this chunk describes the overall function for the h-week ahead forecasting of the subgroup admission rates for Asthma and COPD cases for a given week.

```{r}

num_cores = detectCores()  # Use all but one core
cl = makeCluster(num_cores)
registerDoParallel(cl)

regression_model_fn_subgroups = function(df_link, outcome_var, copd_lag_num = 1, asthma_lag = 1, env_lag = 1, horizon, training_limit=0.5, significant_predictors){
  df = data_editing_subgroups(df_link, outcome_var, significant_predictors = significant_predictors)
  env_variables_to_lag = c("MaxWind", "MeanWind", "MaxTemp", "MinTemp", "MeanTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
  other_disease_var = setdiff(significant_predictors, 
                             c(outcome_var, env_variables_to_lag))
  
  training_length = floor(nrow(df)*training_limit) # Number of observations used for training the data
  initial_theta = 10
  actual_outcome = sub("_([^_]+)$", "", outcome_var)
  last_part = sub(".*_(.*)$", "\\1", outcome_var)
  outcome_var = paste0(actual_outcome,"_overall_rate","_",last_part)
  overall_rate = colnames(df)[str_detect(colnames(df), paste0(actual_outcome,"_overall_rate","_",last_part))]

  filtered_df = df %>% 
    dplyr::select(year,week,outcome_var,all_of(significant_predictors))
  
  regression_model = generate_lagged_df_subgroups(filtered_df, copd_lag_num, asthma_lag, env_lag, outcome = outcome_var)
  X_1 = create_stepped_dataset(regression_model, horizon, outcome = outcome_var)[[1]]
  outcome_var_vec = create_stepped_dataset(regression_model, horizon, outcome = outcome_var)[[2]]
  stepped_df = cbind(X_1, outcome_var_vec) # Combination to form stepped df
  stepped_df = stepped_df %>% rename(!!outcome_var := "outcome_var_vec")
  
  n = nrow(stepped_df) # Length of stepped df
  stepped_df = stepped_df %>%
    mutate(across(everything(), ~ ifelse(is.infinite(.) & . < 0, 0, .)))
  
  # Parallel Processing
  results = foreach(i = (training_length):(n-1), .combine = rbind, .packages = c("dplyr", "mgcv","stringr","gamlss","gamsel","MASS","xgboost","h2o")) %dopar% {
    
    # Standardising variables if it is not the dependent variable and the disease population
    standardize_data = function(train_set, test_set, outcome) {
      # Extract covariate columns (excluding the outcome variable)
      binary_vars = c("heat_wave_week", "hot_week_indicator")
      covariates = setdiff(names(train_set), c(outcome, binary_vars))
  
      # Compute means and standard deviations of covariates from the training set
      train_means = sapply(train_set[covariates], mean, na.rm = TRUE)
      train_sds = sapply(train_set[covariates], sd, na.rm = TRUE)
  
      # Standardize training set
      train_set[covariates] = sweep(train_set[covariates], 2, train_means, "-")
      train_set[covariates] = sweep(train_set[covariates], 2, train_sds, "/")
  
      # Standardize test set using training set parameters
      test_set[covariates] = sweep(test_set[covariates], 2, train_means, "-")
      test_set[covariates] = sweep(test_set[covariates], 2, train_sds, "/")
      # Return standardized datasets
      list(train_set = train_set, test_set = test_set)
    }

    train_set = stepped_df[1:i, ]
    test_set = stepped_df[(i + 1), ]
    testing_set = test_set %>% dplyr::select(-c(outcome_var))
    train_standardised = standardize_data(train_set,testing_set,outcome = outcome_var)[[1]]
    test_standardised = standardize_data(train_set,testing_set,outcome = outcome_var)[[2]]
    
    # Model 1: Pure AR (NO EXOGENOUS VARIABLES)
    if (str_detect(outcome_var,"copd")){
      pure_ar_variables_to_lag = c(paste0("s(",outcome_var))
      pure_ar_lagged_terms = unlist(lapply(pure_ar_variables_to_lag, function(var) {
        paste0(var, "_L", 1:copd_lag_num)
      }))
      pure_ar_formula_str = paste0(outcome_var, " ~ ", paste(paste0(pure_ar_lagged_terms, ")"), collapse = " + "))
      
    } else if (str_detect(outcome_var,"asthma")){
      pure_ar_variables_to_lag = c(paste0("s(",outcome_var))
      pure_ar_lagged_terms = unlist(lapply(pure_ar_variables_to_lag, function(var) {
        paste0(var, "_L", 1:asthma_lag)
      }))
      
      pure_ar_formula_str = paste0(outcome_var, " ~ ", paste(paste0(pure_ar_lagged_terms, ")"), collapse = " + "))
      
    }
    
    pure_ar_model = bam(as.formula(pure_ar_formula_str), family = gaussian(), data = train_standardised)
    pure_ar_predictions = predict(pure_ar_model, newdata = test_standardised, type = "response")
    
    print("Pure AR Done")
    
    # Model 2: AR (Dependent + Other Disease)
    other_disease_var_s = paste0("s(", other_disease_var)
    other_disease_lagged_terms = unlist(lapply(other_disease_var_s, function(var) {
      paste0(var, "_L", 1:asthma_lag)
    }))

    ar_other_disease_formula_str = paste(pure_ar_formula_str, "+", paste(paste0(other_disease_lagged_terms, ")"), collapse = " + "))
    ar_other_disease_model = bam(as.formula(ar_other_disease_formula_str), family = nb(link = "log", theta = initial_theta), data = train_standardised)
    ar_other_disease_predictions = predict(ar_other_disease_model, newdata = test_standardised, type = "response")
    
    print("Other Disease AR Done")
    
    # Model 3: AR (Dependent + Env)
    env_variables_to_lag_s = ifelse(env_variables_to_lag %in% c("hot_week_indicator", "heat_wave_week"), 
                                  env_variables_to_lag, 
                                  paste0("s(", env_variables_to_lag))
    env_lagged_terms = unlist(lapply(env_variables_to_lag_s, function(var) {
      if (startsWith(var, "s(")) {
        paste0(var, "_L", 1:env_lag, ")") # Add lag and closing parenthesis
      } else {
        paste0(var, "_L", 1:env_lag)      # Only add lag for non-smooth terms
      }
    }))
    ar_env_formula_str = paste(pure_ar_formula_str, "+", paste(env_lagged_terms, collapse = " + "))
    ar_env_model = bam(as.formula(ar_env_formula_str), family = nb(link = "log", theta = initial_theta), data = train_standardised)
    ar_env_predictions = predict(ar_env_model, newdata = test_standardised, type = "response")
    print("Env AR Done")
    
    # Model 4: AR (Mixed)
    if (str_detect(outcome_var,"copd")){
      other_disease_var_s = paste0("s(", other_disease_var)
      other_disease_lagged_terms = unlist(lapply(other_disease_var_s, function(var) {
        paste0(var, "_L", 1:asthma_lag)
      }))
    } else if (str_detect(outcome_var,"asthma")){
      other_disease_var_s = paste0("s(", other_disease_var)
      other_disease_lagged_terms = unlist(lapply(other_disease_var_s, function(var) {
        paste0(var, "_L", 1:copd_lag_num)
      }))
    }
    
    env_variables_to_lag_s = ifelse(env_variables_to_lag %in% c("hot_week_indicator", "heat_wave_week"), 
                                  env_variables_to_lag, 
                                  paste0("s(", env_variables_to_lag))
    env_lagged_terms = unlist(lapply(env_variables_to_lag_s, function(var) {
      if (startsWith(var, "s(")) {
        paste0(var, "_L", 1:env_lag, ")") # Add lag and closing parenthesis
      } else {
        paste0(var, "_L", 1:env_lag)      # Only add lag for non-smooth terms
      }
    }))
    
    # Create the formula string
    ar_env_formula_str = paste(pure_ar_formula_str, "+", paste(env_lagged_terms, collapse = " + "))
    
    ar_mixed_formula_str = paste(pure_ar_formula_str, "+", paste(env_lagged_terms, collapse = " + "),"+", paste(paste0(other_disease_lagged_terms, ")"), collapse = " + "))
    
    ar_mixed_model = bam(as.formula(ar_mixed_formula_str), family = gaussian(), data = train_standardised)
    ar_mixed_predictions = predict(ar_mixed_model, newdata = test_standardised, type = "response")
    
    print("AR (Mixed) Done")
    
    # Model 5: GAMLSS Model
    
    mean_matched_columns = unlist(lapply(significant_predictors, function(predictor) {
      grep(predictor, colnames(stepped_df), value = TRUE)
    }))
    
    if (str_detect(outcome_var,"copd")){
      outcome_variables_to_lag = c(paste0("pb(",outcome_var))
      
      outcome_lagged_terms = unlist(lapply(outcome_variables_to_lag, function(var) {
        paste0(var, "_L", 1:copd_lag_num)
      }))
      
      base_terms = paste0(outcome_var, " ~ ", paste(paste0(outcome_lagged_terms, ")"), collapse = " + "))
    } else if (str_detect(outcome_var,"asthma")){
      outcome_variables_to_lag = c(paste0("pb(",outcome_var))
      
      outcome_lagged_terms = unlist(lapply(outcome_variables_to_lag, function(var) {
        paste0(var, "_L", 1:asthma_lag)
      }))
      
      base_terms = paste0(outcome_var, " ~ ", paste(paste0(outcome_lagged_terms, ")"), collapse = " + "))
    }
    
    mean_terms = paste0("pb(", mean_matched_columns, ")")
    mu_formula_string = paste(c(base_terms, mean_terms), collapse = " + ")
    overall_formula = as.formula(mu_formula_string)
    
    gam_lss_predictions = tryCatch({
    # Fit the GAMLSS model and make predictions if no error
    gam_lss_obj = gamlss(overall_formula, family = NO(), data = train_standardised)
    predict(object = gam_lss_obj,
            what = "mu",
            data = train_standardised, newdata = test_standardised, type = "response")
    }, error = function(e) {
    # If an error occurs, return NA
    cat("Error: ", e$message, "\n")
    return(NA)
    })
    
    print("GAMLSS Done")
    
    # Model 6: 2-step forecasting: GLM-GAMSEL
    
    # Stage 1 of Model 6: GLM
    if (str_detect(outcome_var,"copd")){
      pure_ar_variables_to_lag_ns = c(outcome_var)
      pure_ar_lagged_terms_ns = unlist(lapply(pure_ar_variables_to_lag_ns, function(var) {
        paste0(var, "_L", 1:copd_lag_num)
      }))
      
      pure_ar_formula_str_ns = paste0(outcome_var, " ~ ", paste(pure_ar_lagged_terms_ns, collapse = " + "))
      
      other_disease_var_ns = other_disease_var
      other_disease_lagged_terms_ns = unlist(lapply(other_disease_var_ns, function(var) {
        paste0(var, "_L", 1:asthma_lag)
      }))
    } else if (str_detect(outcome_var,"asthma")){
      pure_ar_variables_to_lag_ns = c(outcome_var)
      pure_ar_lagged_terms_ns = unlist(lapply(pure_ar_variables_to_lag_ns, function(var) {
        paste0(var, "_L", 1:asthma_lag)
      }))
      
      pure_ar_formula_str_ns = paste0(outcome_var, " ~ ", paste(pure_ar_lagged_terms_ns, collapse = " + "))
      
      other_disease_var_ns = other_disease_var
      other_disease_lagged_terms_ns = unlist(lapply(other_disease_var_ns, function(var) {
        paste0(var, "_L", 1:copd_lag_num)
      }))
    }
    env_variables_to_lag_ns = env_variables_to_lag
    env_lagged_terms_ns = unlist(lapply(env_variables_to_lag_ns, function(var) {
      paste0(var, "_L", 1:env_lag)
      }))
    
    ar_mixed_formula_str_ns = paste(pure_ar_formula_str_ns, "+", paste(env_lagged_terms_ns, collapse = " + "),"+", paste(other_disease_lagged_terms_ns, collapse = " + "))
    glm_training_set = train_standardised %>% dplyr::select(-c(outcome_var)) # Used to generate residuals from training set
    glm_model = glm(as.formula(ar_mixed_formula_str_ns), family = gaussian(), data = train_standardised)
    glm_train_pred = predict(glm_model, newdata = glm_training_set, type = "response")
    glm_residuals = train_standardised[[outcome_var]] - glm_train_pred
    glm_pred = predict(glm_model, newdata = test_standardised, type = "response") # Making predictions for test set in first step
    
    # Stage 2 of Model 6: GAMSEL
    
    # Removal of population offset (different outcome variable; no need offset) and Creation of Pseudo Bases for Variables
    gamsel_training = train_standardised %>% dplyr::select(-c(outcome_var))
    unique_vals = sapply(gamsel_training, function(col) length(unique(col)))
    degrees = sapply(unique_vals, function(u) if (u <= 2) 1 else min(u - 1, 8))
    dfs = pmin(degrees, unique_vals - 1)
    a_bases = pseudo.bases(gamsel_training, degree = degrees, df = dfs)
    
    # Conversion of formatting for GAMSEL and finding optimal values
    train_matrix = as.matrix(train_standardised %>% dplyr::select(-c(outcome_var)))
    new_outcome = as.matrix(glm_residuals)
    gaussian_gamsel = gamsel(train_matrix, new_outcome, bases=a_bases) # Training GAMSEL
    optimal_lambda = which.max(gaussian_gamsel$dev.ratio)
    testing_set_gamsel = test_standardised
    residual_pred = predict(gaussian_gamsel, newdata = testing_set_gamsel, type="response")[optimal_lambda]
    if (abs(residual_pred) > 50){ 
      residual_pred = 0
    }
    glm_gamsel_predictions = glm_pred + residual_pred
    
    # Model 7: 2-step forecasting: GAM-XGBoost
    
    # Stage 1 of Model 7: GAM
    training_set = train_standardised %>% dplyr::select(-c(outcome_var))
    
    gam_model = bam(as.formula(ar_mixed_formula_str), family = gaussian(), data = train_standardised)
    gam_pred = predict(gam_model, newdata = test_standardised, type = "response")
    gam_train_pred = predict(gam_model, newdata = training_set, type = "response") 
    err = abs(train_standardised[[outcome_var]] - gam_train_pred)/train_standardised[[outcome_var]]
    
    # Generation of Residuals
    gam_residuals = train_standardised[[outcome_var]] - gam_train_pred 
    train_set_xgboost = train_standardised %>% mutate(gam_residuals = gam_residuals)
    
    # Stage 2 of Model 7: XGBoost
    xgboost_formula = as.formula(paste0("gam_residuals ~ ", paste(pure_ar_lagged_terms_ns, collapse = " + ")," + ", paste(env_lagged_terms_ns, collapse = " + ")," + ", paste(other_disease_lagged_terms_ns, collapse = " + ")))
    xgboost_formula_test = as.formula(paste0("~", paste(pure_ar_lagged_terms_ns, collapse = " + ")," + ", paste(env_lagged_terms_ns, collapse = " + ")," + ", paste(other_disease_lagged_terms_ns, collapse = " + ")))
    
    train_matrix = model.matrix(xgboost_formula, data = train_set_xgboost)[, -1]
    test_matrix = model.matrix(xgboost_formula_test, data = test_standardised)[, -1]
    print(xgboost_formula)
    print(xgboost_formula_test)
    if (nrow(as.data.frame(t(test_matrix)))==1){
      test_matrix = as.matrix(t(test_matrix))
    } else{
      test_matrix = as.matrix(test_matrix)
    }
    
    y_train = train_set_xgboost$gam_residuals
    train_matrix = as.matrix(train_matrix)
    
    xgb_train = xgb.DMatrix(data = train_matrix, label = y_train)
    
    xgb_model = xgboost(
      data = xgb_train,
      objective = "reg:squarederror",  # Regression objective
      nrounds = 100,  # Number of boosting rounds (can tune this)
      max_depth = 6,  # Maximum tree depth
      eta = 0.1,  # Learning rate
      subsample = 0.8,  # Subsample ratio of the training instances
      colsample_bytree = 0.8,  # Subsample ratio of columns
      verbosity = 0  # Suppress output
    )
    
    residual_pred = predict(xgb_model, newdata = xgb.DMatrix(data = test_matrix))
    gam_xgboost_predictions = gam_pred + residual_pred
    
    print("GAM-XGBoost Done")
    
    # Model 8: MLP with AutoML
    
    train_standardised_automl = train_standardised
    test_standardised_automl = standardize_data(train_set,test_set,outcome = outcome_var)[[2]]
    test_standardised_automl = test_standardised_automl
    
    h2o.init()
    train_set = as.h2o(train_standardised_automl)
    
    aml_test_set = as.h2o(test_standardised_automl)

    predictors = setdiff(names(train_standardised_automl), c(outcome_var))
    response = outcome_var

    # Train Deep Learning Model
    aml = h2o.deeplearning(
      x = predictors, y = response,
      training_frame = train_set,
      seed = 123
    )
    
    aml_prediction = as.data.frame(h2o.predict(aml, newdata = aml_test_set))[1,]
    actual_value = as.data.frame(aml_test_set[[response]])[1,]
    
    result_row = data.frame(
      actual = test_set[[outcome_var]],
      pure_ar_predictions = pure_ar_predictions,
      ar_mixed_predictions = ar_mixed_predictions,
      gam_lss_predictions = gam_lss_predictions,
      glm_gamsel_predictions = glm_gamsel_predictions,
      gam_xgboost_predictions = gam_xgboost_predictions,
      aml_prediction = aml_prediction)
    message(paste("Completed iteration:", i))
    return(result_row)
  }
  return(results)
}
```

Finally, running of the code then commences for the subgroup admission rates for COPD and Asthma in hospitals.
```{r}
all_asthma_subgroup_factors = c("female", "male", "age_15_to_39","age_40_to_54", 
                                "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")
all_copd_subgroup_factors = c("female", "male","age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")

for (asthma_factor in all_asthma_subgroup_factors){
  for (horizon in 1:12){
    full_asthma_factor = paste0(asthma_factor,"_asthma")
    print(paste("Starting", full_asthma_factor, "horizon",horizon))
    submodels_asthma = regression_model_fn_subgroups(df_link = "combined_asthma_env_080225_norates.csv",outcome_var = full_asthma_factor,horizon=horizon,significant_predictors = asthma_discharge_significant_predictors)
    asthma_file_str = paste0("asthma_", asthma_factor, horizon,"_new.rdata")
    save(submodels_asthma, file = asthma_file_str)
    print(paste("horizon",horizon,"for", full_asthma_factor, "done"))
  }
}

for (copd_factor in all_copd_subgroup_factors){
  for (horizon in 1:12){
    full_copd_factor = paste0(copd_factor,"_copd")
    print(paste("Starting", full_copd_factor,"horizon",horizon))
    submodels_copd = regression_model_fn_subgroups(df_link = "combined_asthma_env_080225_norates.csv",outcome_var = full_copd_factor,horizon=horizon, significant_predictors = copd_discharge_significant_predictors)
    copd_file_str = paste0("copd_", copd_factor, horizon,"_new.rdata")
    save(submodels_copd, file = copd_file_str)
    print(paste("horizon",horizon,"for",full_copd_factor, "done"))
  }
}

```
