---
title: "04a combinations (analysis 1)"
output: html_document
date: "2024-11-11"
---

Loading of libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library()
rm(list=ls())
library(tidyverse)

copd_discharge_significant_predictors = c("cases_asthma", "female_overall_rate_asthma", "male_overall_rate_asthma", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall","age_15_to_39_overall_rate_asthma", "age_40_to_54_overall_rate_asthma", "age_55_to_64_overall_rate_asthma", "age_65_to_74_overall_rate_asthma", "age_75_to_84_overall_rate_asthma", "age_85_above_overall_rate_asthma")

asthma_discharge_significant_predictors = c("cases_copd", "female_overall_rate_copd", "male_overall_rate_copd", "age_55_to_64_overall_rate_copd", "age_65_to_74_overall_rate_copd", "age_75_to_84_overall_rate_copd","age_85_above_overall_rate_copd", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
```

# Description of File

In this coding file, two analyses were conducted:

## Analysis 1: Multi-Step Forecasting for Raw Admissions' cases for COPD and Asthma patients
Given that the running of models have all been labelled as submodels_copd or submodels_asthma for each horizon, the following steps must be done:
(1) Renaming of function to admission_rate_(disease)(horizon_num)_(exog/nonexog)_090325 must be done to distinguish between the horizons, and variables. For the exogenous model, the ensemble forecasts must be constructed AGAIN since a different number of models are used for this comparison
(2) Combination of horizons to a single dataset (should have 3666 observations)
(3) Construction of superensemble models based on the individual models

Additionally, the Naive method was added through the addition_of_naive function as well.

## Analysis 2: Multi-Step Forecasting for Subgroup admission rates for COPD and Asthma patients
Given that the running of models have all been labelled as submodels_copd or submodels_asthma for each horizon, the following steps must be done:
(1) Renaming of function to admission_rate_(disease)(horizon_num)_(exog/nonexog)_090325 must be done to distinguish between the horizons, and variables. For the exogenous model, the ensemble forecasts must be constructed AGAIN since a different number of models are used for this comparison
(2) Combination of horizons to a single dataset (should have 3666 observations)
(3) Construction of superensemble models based on the individual models

Additionally, the Naive method was added through the addition_of_naive function as well.

Now, we begin on coding the model:

## Functions in Analysis 1
- Data Editing Function --> removes irrelevant variables
- Naive Model Function
- Generation of Naive model dataset
```{r}
data_editing_cases = function(df_filename, outcome, significant_predictors){
  combined_df = read_csv(df_filename)%>%
  column_to_rownames(var = "...1")
  
  if (outcome == "cases_copd"){
    popn = "residents_copd"
  } else if (outcome == "cases_asthma"){
    popn = "residents_asthma"
  } else {
    actual_outcome = sub("_([^_]+)$", "", outcome)
    last_part = sub(".*_(.*)$", "\\1", outcome)
    popn = colnames(combined_df)[str_detect(colnames(combined_df), paste0(actual_outcome,"_residents","_",last_part))]
  }
  new_combined = combined_df %>% 
    dplyr::select(year, week, outcome, popn, significant_predictors)
  if (outcome == "male_asthma"|outcome=="male_copd"){
    new_combined = new_combined %>% 
      dplyr::select(-starts_with("female_residents"))
  }
  return(new_combined)
}

naive_model = function(df, horizon, outcome){
  df[[outcome]] = dplyr::lag(df[[outcome]],n=horizon)
  df = na.omit(df)
  return(df)
}

addition_of_naive = function(df_link, outcome_var, disease, copd_lag_num = 1, asthma_lag = 1, env_lag = 1, horizon, training_limit=0.5, significant_predictors){
  df = data_editing_cases(df_link, outcome_var, significant_predictors = significant_predictors)
  env_variables_to_lag = c("MaxWind", "MeanWind", "MaxTemp", "MinTemp", "MeanTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
  other_disease_var = setdiff(significant_predictors, 
                             c(outcome_var, env_variables_to_lag))
  # return(df)
  training_length = floor(nrow(df)*training_limit) # Number of observations used for training the data
  if (str_detect(outcome_var,"copd")){
    disease_popn = "residents_copd"
    lagged_disease_popn = "residents_copd_L1"
  } else if (str_detect(outcome_var,"asthma")){
    disease_popn = "residents_asthma"
    lagged_disease_popn = "residents_asthma_L1"
  }
  # Model 1: Naive Model
  naive_x = naive_model(df,horizon,outcome = outcome_var)[[outcome_var]]
  naive_y = df[(horizon+1):nrow(df),][[outcome_var]]
  naive_x = naive_x[(training_length+1):length(naive_x)]
  naive_y = naive_y[(training_length+1):length(naive_y)]
  naive_pred = naive_x
  naive_actual = naive_y
  
  # Generation of error dataframe
  comparison_df = data.frame(
    actual = naive_actual,
    naive_predictions = naive_pred
  )
  return(comparison_df)
}

# x = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", outcome_var = "female_overall_rate_asthma", disease = "asthma", horizon = 1, significant_predictors = asthma_discharge_significant_predictors)
```

## Combination of Models

The following 2 steps are performed below:
- Renaming of variables (from submodels_(disease) to new name)
- Addition of Naive model
```{r setup, include=FALSE}
asthma_variables = c("female", "male", "cases", "age_15_to_39", "age_40_to_54", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")
copd_variables = c("female", "male", "cases", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")

renaming_fn = function(vec, disease){
  if (disease == "copd"){
    for (var in vec){
      if (var == "cases"){
        var_name = paste0(var,"_", disease)
      } else {
        var_name = paste0(var,"_overall_rate_", disease)
      }
      for (horizon in 1:12) {
        file_name = paste0(disease, "_", var, horizon, "_new.rdata")
        load(file_name)
        
        combined_copd_df = submodels_copd
        
        comparison_df = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", disease = disease, outcome_var = var_name,horizon=horizon,significant_predictors = copd_discharge_significant_predictors)
        if (identical(combined_copd_df$actual, comparison_df$actual)) {
            final_df = cbind(combined_copd_df, comparison_df%>% dplyr::select(-actual))
        }
        
        combined_name_copd = paste0(var, "_", disease, horizon, "_270225")
        assign(combined_name_copd, final_df)
        save_file_name = paste0(combined_name_copd, ".rdata")
        save(list = combined_name_copd, file = save_file_name)
      }
    }
  } else if (disease == "asthma"){
    for (var in vec){
      if (var == "cases"){
        var_name = paste0(var,"_", disease)
      } else {
        var_name = paste0(var,"_overall_rate_", disease)
      }
      for (horizon in 1:12) {
        file_name = paste0(disease, "_", var, horizon, "_new.rdata")
        load(file_name)
        combined_asthma_df = submodels_asthma
        
        comparison_df = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", disease = disease, outcome_var = var_name,horizon=horizon,significant_predictors = asthma_discharge_significant_predictors)
        if (identical(combined_asthma_df$actual, comparison_df$actual)) {
            final_df = cbind(combined_asthma_df, comparison_df%>% dplyr::select(-actual))
        }
        
        combined_name_asthma = paste0(var, "_", disease, horizon, "_270225")
        assign(combined_name_asthma, final_df)
        save_file_name = paste0(combined_name_asthma, ".rdata")
        save(list = combined_name_asthma, file = save_file_name)
      }
    }
  }
  return("Done")
}

renaming_fn(copd_variables, "copd")
renaming_fn(asthma_variables, "asthma")
```

After renaming, the generation of a combined dataframe was done across all possible horizons. This was performed separately for cases and subgroups. Hence, there are two parts in this chunk.

Part 1: Combination for cases
Part 2: Combination for subgroups
```{r}
rm(list=ls())

# Extraction of column names
file_name = paste0("cases_copd", 7, "_270225.rdata")
load(file_name)
initial_col_names = colnames(cases_copd7_270225)
temp_df = get(paste0("cases_copd", 7, "_270225"))
temp_df$index = seq_len(nrow(temp_df))
temp_df$horizon = 7
col_names = colnames(temp_df)

## Part 1: Raw admissions cases Combination
cases_var = "cases"

for (var in cases_var){
  df_combined = data.frame(matrix(ncol = 12, nrow = 0))
  colnames(df_combined) = col_names
  
  for (horizon in 1:12) {
    file_name = paste0(var, "_copd", horizon, "_270225.rdata")
    load(file_name)
    temp_df = get(paste0(var, "_copd", horizon, "_270225"))
    rownames(temp_df) = NULL
    colnames(temp_df) = initial_col_names
    temp_df$index = seq_len(nrow(temp_df))
    temp_df$horizon = horizon
    df_combined = rbind(df_combined, temp_df)
  }
  final_df = df_combined %>%
      rename("aml_predictions" = "aml_prediction") %>%
      tidyr::fill(gam_lss_predictions, .direction = "down")
  combined_name_copd_var = paste0("copd_", var, "_combined_270225")
  assign(combined_name_copd_var, final_df)
  save_file_name = paste0(combined_name_copd_var, ".rdata")
  save(list = combined_name_copd_var, file = save_file_name)
}

for (var in cases_var){
  combined_df = data.frame(matrix(ncol = 14, nrow = 0))
  colnames(combined_df) = col_names
  for (horizon in 1:12) {
    file_name = paste0(var, "_asthma", horizon, "_270225.rdata")
    load(file_name)
    temp_df = get(paste0(var, "_asthma", horizon, "_270225"))
    rownames(temp_df) = NULL
    colnames(temp_df) = initial_col_names
    temp_df$index = seq_len(nrow(temp_df))
    temp_df$horizon = horizon
    combined_df = rbind(combined_df, temp_df)
  }
  final_df = combined_df %>%
      rename("aml_predictions" = "aml_prediction") %>%
      tidyr::fill(gam_lss_predictions, .direction = "down")
  combined_name_asthma_var = paste0("asthma_", var, "_combined_270225")
  assign(combined_name_asthma_var, final_df)
  save_file_name = paste0(combined_name_asthma_var, ".rdata")
  save(list = combined_name_asthma_var, file = save_file_name)
}

## Part 2: Subgroups 
asthma_variables = c("female", "male", "age_15_to_39", "age_40_to_54", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")
copd_variables = c("female", "male", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")

file_name = paste0("female_copd", 7, "_270225.rdata")
load(file_name)
initial_col_names = colnames(female_copd7_270225)
temp_df = get(paste0("female_copd", 7, "_270225"))
temp_df$index = seq_len(nrow(temp_df))
temp_df$horizon = 7
col_names = colnames(temp_df)

for (var in copd_variables){
  df_combined = data.frame(matrix(ncol = 10, nrow = 0))
  colnames(df_combined) = col_names
  
  for (horizon in 1:12) {
    file_name = paste0(var, "_copd", horizon, "_270225.rdata")
    load(file_name)
    temp_df = get(paste0(var, "_copd", horizon, "_270225"))
    temp_df$index = seq_len(nrow(temp_df))
    temp_df$horizon = horizon
    rownames(temp_df) = NULL
    colnames(temp_df) = col_names
    df_combined = rbind(df_combined, temp_df)
  }
  final_df = df_combined %>%
      rename("aml_predictions" = "aml_prediction") %>%
      tidyr::fill(gam_lss_predictions, .direction = "down")
  combined_name_copd_var = paste0("copd_", var, "_subgroups_combined_270225")
  assign(combined_name_copd_var, final_df)
  save_file_name = paste0(combined_name_copd_var, ".rdata")
  save(list = combined_name_copd_var, file = save_file_name)
}

asthma_variables = c("female", "male", "age_15_to_39", "age_40_to_54", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")
for (var in asthma_variables){
  combined_df = data.frame(matrix(ncol = 10, nrow = 0))
  colnames(combined_df) = col_names
  for (horizon in 1:12) {
    file_name = paste0(var, "_asthma", horizon, "_270225.rdata")
    load(file_name)
    temp_df = get(paste0(var, "_asthma", horizon, "_270225"))
    temp_df$index = seq_len(nrow(temp_df))
    temp_df$horizon = horizon
    rownames(temp_df) = NULL
    colnames(temp_df) = col_names
    combined_df = rbind(combined_df, temp_df)
  }
  final_df = combined_df %>%
      rename("aml_predictions" = "aml_prediction") %>%
      tidyr::fill(gam_lss_predictions, .direction = "down")
  combined_name_asthma_var = paste0("asthma_", var, "_subgroups_combined_270225")
  assign(combined_name_asthma_var, final_df)
  save_file_name = paste0(combined_name_asthma_var, ".rdata")
  save(list = combined_name_asthma_var, file = save_file_name)
}
```

## Generation of Superensemble Models

As explained in the paper, there are 5 different methods used to generate forecast combinations from the individual models. The individual methods are described below:

- Method 1: Equal Weights
- Method 2: Median Weights
- Method 3: Bates and Granger --> Inverse SE
- Method 4: Bates and Granger --> Inverse Cumulative SE (Expanding Window)
- Method 5: Trimmed Mean

The functions involved in superensemble generation are first listed below:
```{r}

bates_granger_method_1 = function(df){
  model_names = colnames(df)

  # Filter names ending with "predictions" and remove the suffix
  new_names = model_names %>%
    str_subset("predictions$") %>%
    str_remove("_predictions")
  
  final_df = df %>%
    # group_by(horizon) %>%
    rowwise() %>%
    mutate(across(ends_with("predictions"), ~ (. - actual)^2, .names = "se_{str_remove(.col, '_predictions')}"),
           across(ends_with("predictions"), ~ 1/((. - actual)^2), .names = "inv_se_{str_remove(.col, '_predictions')}"),
           inv_se_sum = sum(c_across(starts_with("inv_se_")), na.rm = TRUE),
           across(starts_with("inv_se_"), ~ ./inv_se_sum, .names = "norm_{str_remove(.col, '_predictions')}"),
           across(starts_with("norm_"), ~if_else(is.nan(.), 1, .)))
  
  pred_col = paste0(new_names, "_predictions")
  norm_col = paste0("norm_inv_se_", new_names)
  pred_norm = final_df %>% dplyr::select(pred_col,norm_col,horizon)
  # return(pred_norm)
  final_weighted_preds = rowSums(map2_dfc(pred_col, norm_col, ~ {
    pred_norm[[.x]] * pred_norm[[.y]]
  }), na.rm = TRUE)
  
  return(final_weighted_preds)
}

bates_granger_method_2 = function(df){
  model_names = colnames(df)

  # Filter names ending with "predictions" and remove the suffix
  new_names = model_names %>%
    str_subset("predictions$") %>%
    str_remove("_predictions")
  
  final_df = df %>%
    rowwise() %>%
    mutate(across(ends_with("predictions"), ~ (. - actual)^2, .names = "se_{str_remove(.col, '_predictions')}")) %>%
    ungroup() %>%
    group_by(horizon) %>%
    mutate(across(starts_with("se"), cumsum, .names = "cumsum_{str_remove(.col, '_predictions')}")) %>%
    ungroup() %>%
    rowwise() %>%
    mutate(across(starts_with("cumsum_"), ~ 1/., .names = "inv_{str_remove(.col, '_predictions')}"),
           inv_se_sum = sum(c_across(starts_with("inv_cumsum_")), na.rm = TRUE),
           across(starts_with("inv_cumsum_se_"), ~ ./inv_se_sum, .names = "norm_{str_remove(.col, '_predictions')}"),
           across(starts_with("norm_"), ~if_else(is.nan(.), 1, .)))
  # return(final_df)
  pred_col = paste0(new_names, "_predictions")
  norm_col = paste0("norm_inv_cumsum_se_", new_names)
  pred_norm = final_df %>% dplyr::select(pred_col,norm_col)
  # return(pred_norm)
  final_weighted_preds = rowSums(map2_dfc(pred_col, norm_col, ~ {
    pred_norm[[.x]] * pred_norm[[.y]]
  }), na.rm = TRUE)
  return(final_weighted_preds)
}

superensem_generator = function(df){
  bg1_predictions = bates_granger_method_1(df)
  bg2_predictions = bates_granger_method_2(df)
  
  final_df = df %>%
    rowwise() %>%
    mutate(eq_weights_predictions = rowMeans(across(ends_with("predictions")), na.rm = TRUE),
           med_weights_predictions = median(c_across(ends_with("predictions")), na.rm = TRUE),
           trimmed_mean_predictions = mean(  c_across(ends_with("predictions")), 
      trim = 0.1,  # 10% trimmed mean
      na.rm = TRUE))
  final_df$bg1_predictions = bg1_predictions
  final_df$bg2_predictions = bg2_predictions
  return(final_df)
}
```

Now, we will then run the combinations across all dataframes
```{r}
for (var in copd_variables){
  file_name = paste0("copd_", var, "_combined_280225.rdata")
  load(file_name)
  df = get(paste0("copd_", var, "_combined_280225"))
  final_df = superensem_generator(df)
  combined_name = paste0("copd_", var, "_all_280225")
  assign(combined_name, final_df)
  save_file_name = paste0(combined_name, ".rdata")
  save(list = combined_name, file = save_file_name)
}

for (var in asthma_variables){
  file_name = paste0("asthma_", var, "_combined_280225.rdata")
  load(file_name)
  df = get(paste0("asthma_", var, "_combined_280225"))
  final_df = superensem_generator(df)
  combined_name = paste0("asthma_", var, "_all_280225")
  assign(combined_name, final_df)
  save_file_name = paste0(combined_name, ".rdata")
  save(list = combined_name, file = save_file_name)
}

```
