---
title: "04 combinations"
output: html_document
date: "2024-11-11"
---

In this coding file, two analyses were conducted:

# Analysis 1: Comparing forecasts with exogenous variables AGAINST forecasts without exogenous variables
- In this analysis, only Naive, AR, GAMLSS, GLM-GAMSEL, GAM-XGBoost, and MLP are used to compare the 2 models. For AR, exogenous variables use the AR (Mixed) model, while it is AR (Pure) model for without exogenous variables.

Given that the running of models have all been labelled as submodels_copd or submodels_asthma for each horizon, the following steps must be done:
(1) Renaming of function to admission_rate_(disease)(horizon_num)_(exog/nonexog)_090325 must be done to distinguish between the horizons, and variables. For the exogenous model, the ensemble forecasts must be constructed AGAIN since a different number of models are used for this comparison
(2) Combination of horizons to a single dataset (should have 3666 observations)
(3) Construction of superensemble models based on the individual models
(4) Addition of the Naive model

This means that there will be a total of 2 models produced, one using exogenous variables, and another without exogenous variables.

# Analysis 2: Comparing subgroup analyses effectiveness between AGGREGATED forecasts and TOTAL forecasts
- In this analysis, it compares AGGREGATED forecasts (individually predicted subgroup rates, then aggregated) and TOTAL forecasts (directly forecasting the total forecasts)
- AGGREGATED forecasts have already been constructed (since submodel rates have already been forecasted prior to this) and TOTAL forecasts have been done (forecasting of overall rates)
- So what this analysis does is to perform the following steps
(1) Usage of only AR, GAMLSS, GLM-GAMSEL, GAM-XGBoost, and MLP models
(2) Code out process to construct aggregated forecast --> aggregated forecast = (individual forecasts * subgroup population) / (overall disease population)
(3) Based on the models used, construct superensembles
(4) Repeat for GENDER and AGE subgroups

This means that there will be a total of 4 different models, which are...

Model A1 - Age Total Forecast
Model A2 - Age Aggregated Forecast
Model B1 - Gender Total Forecast
Model B2 - Gender Aggregated Forecast

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library()
rm(list=ls())
library(tidyverse)

copd_discharge_significant_predictors = c("female_asthma", "male_asthma", "cases_asthma", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall","age_15_to_39_asthma", "age_40_to_54_asthma","age_55_to_64_asthma","age_65_to_74_asthma", "age_75_to_84_asthma")

asthma_discharge_significant_predictors = c("female_copd", "male_copd", "age_55_to_64_copd", "age_65_to_74_copd", "age_75_to_84_copd","age_85_above_copd", "cases_copd", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
```

## Analysis 1: Exogenous vs Non-Exogenous

Part 1: Addition of Naive model
Part 2: Renaming Variables
Part 3: Combination into a single horizon
Part 4: Generation of Superemsemble models

```{r}
data_editing_cases = function(df_filename, outcome, significant_predictors){
  combined_df = read_csv(df_filename)%>%
  column_to_rownames(var = "...1")
  
  if (outcome == "cases_copd"){
    popn = "residents_copd"
  } else if (outcome == "cases_asthma"){
    popn = "residents_asthma"
  } else {
    actual_outcome = sub("_([^_]+)$", "", outcome)
    last_part = sub(".*_(.*)$", "\\1", outcome)
    popn = colnames(combined_df)[str_detect(colnames(combined_df), paste0(actual_outcome,"_residents","_",last_part))]
  }
  new_combined = combined_df %>% 
    dplyr::select(year, week, outcome, popn, significant_predictors)
  if (outcome == "male_asthma"|outcome=="male_copd"){
    new_combined = new_combined %>% 
      dplyr::select(-starts_with("female_residents"))
  }
  return(new_combined)
}

naive_model = function(df, horizon, outcome){
  df[[outcome]] = dplyr::lag(df[[outcome]],n=horizon)
  df = na.omit(df)
  return(df)
}

addition_of_naive = function(df_link, outcome_var, disease, copd_lag_num = 1, asthma_lag = 1, env_lag = 1, horizon, training_limit=0.5, significant_predictors){
  df = data_editing_cases(df_link, outcome_var, significant_predictors = significant_predictors)
  env_variables_to_lag = c("MaxWind", "MeanWind", "MaxTemp", "MinTemp", "MeanTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
  other_disease_var = setdiff(significant_predictors, 
                             c(outcome_var, env_variables_to_lag))
  # return(df)
  training_length = floor(nrow(df)*training_limit) # Number of observations used for training the data
  if (str_detect(outcome_var,"copd")){
    disease_popn = "residents_copd"
    lagged_disease_popn = "residents_copd_L1"
  } else if (str_detect(outcome_var,"asthma")){
    disease_popn = "residents_asthma"
    lagged_disease_popn = "residents_asthma_L1"
  }
  # Model 1: Naive Model
  naive_x = naive_model(df,horizon,outcome = outcome_var)[[outcome_var]]
  naive_y = df[(horizon+1):nrow(df),][[outcome_var]]
  naive_x = naive_x[(training_length+1):length(naive_x)]
  naive_y = naive_y[(training_length+1):length(naive_y)]
  naive_pred = naive_x
  naive_actual = naive_y
  
  # Generation of error dataframe
  comparison_df = data.frame(
    actual = naive_actual,
    naive_predictions = naive_pred
  )
  return(comparison_df)
}

# x = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", outcome_var = "female_overall_rate_asthma", disease = "asthma", horizon = 1, significant_predictors = asthma_discharge_significant_predictors)
```

CHUNK 1: FOR NON-EXOGENOUS VARIABLES
```{r setup, include=FALSE}
# Part 1: Renaming variables

variables = c("noexog")

renaming_fn = function(vec, disease){
  if (disease == "copd"){
    for (var in vec){
      for (horizon in 1:12) {
        file_name = paste0("admission_rate_", disease, horizon, "_", var, "_050325.rdata")
        load(file_name)
        combined_copd_df = submodels_copd
        
        # Addition of Naive model
        comparison_df = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", disease = disease, outcome_var = "overall_rate_copd",horizon=horizon,significant_predictors = copd_discharge_significant_predictors)
        if (identical(combined_copd_df$actual, comparison_df$actual)) {
            final_df = cbind(combined_copd_df, comparison_df%>% dplyr::select(-actual))
        }
        
        combined_name_copd = paste0("admission_rate_", disease, horizon, "_", var, "_090325")
        assign(combined_name_copd, final_df)
        save_file_name = paste0(combined_name_copd, ".rdata")
        save(list = combined_name_copd, file = save_file_name)
      }
    }
  } else if (disease == "asthma"){
    for (var in vec){
      for (horizon in 1:12) {
        file_name = paste0("admission_rate_", disease, horizon, "_", var, "_050325.rdata")
        load(file_name)
        combined_asthma_df = submodels_asthma
        
        # Addition of Naive model
        comparison_df = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", disease = disease, outcome_var = "overall_rate_asthma",horizon=horizon,significant_predictors = asthma_discharge_significant_predictors)
        if (identical(combined_asthma_df$actual, comparison_df$actual)) {
            final_df = cbind(combined_asthma_df, comparison_df%>% dplyr::select(-actual))
        }
        
        combined_name_asthma = paste0("admission_rate_", disease, horizon, "_", var, "_090325")
        assign(combined_name_asthma, final_df)
        save_file_name = paste0(combined_name_asthma, ".rdata")
        save(list = combined_name_asthma, file = save_file_name)
      }
    }
  }
  return("Done")
}

renaming_fn(variables, "copd")
renaming_fn(variables, "asthma")

# Part 2: Combination to a single dataframe
rm(list=ls())
file_name = paste0("admission_rate_asthma12_noexog_090325.rdata")
load(file_name)
no_exog_initial_col_names = colnames(admission_rate_asthma12_noexog_090325)
no_exog_temp_df = get(paste0("admission_rate_asthma12_noexog_090325"))
no_exog_temp_df$index = seq_len(nrow(no_exog_temp_df))
no_exog_temp_df$horizon = 7
no_exog_col_names = colnames(no_exog_temp_df)
no_exog_len = length(no_exog_col_names)

for (disease in c("copd","asthma")){
  overall_df_combined = data.frame(matrix(ncol = no_exog_len, nrow = 0))
  colnames(overall_df_combined) = no_exog_col_names
  for (horizon in 1:12) {
    file_name = paste0("admission_rate_", disease, horizon, "_noexog", "_090325.rdata")
    load(file_name)
    temp_df = get(paste0("admission_rate_", disease, horizon, "_noexog", "_090325"))
    rownames(temp_df) = NULL
    colnames(temp_df) = no_exog_initial_col_names
    temp_df$index = seq_len(nrow(temp_df))
    temp_df$horizon = horizon
    overall_df_combined = rbind(overall_df_combined, temp_df)
  }
  overall_final_df = overall_df_combined %>%
    rename("aml_predictions" = "aml_prediction") %>%
    tidyr::fill(gam_lss_predictions, .direction = "down")
  combined_name_var = paste0(disease, "_noexog", "_combined_090325")
  assign(combined_name_var, overall_final_df)
  save_file_name = paste0(combined_name_var, ".rdata")
  save(list = combined_name_var, file = save_file_name)
}

```

CHUNK 2: FOR EXOGENOUS VARIABLES
- In this chunk, selection was made based on the models used for superensemble generation
```{r}
# Part 1: Renaming variables

variables = c("exog")

renaming_fn = function(vec, disease){
  if (disease == "copd"){
    for (var in vec){
      for (horizon in 1:12) {
        file_name = paste0("admission_rate_", disease, horizon, "_", var, "_050325.rdata")
        load(file_name)
        combined_copd_df = submodels_copd
        
        # Addition of Naive model
        comparison_df = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", disease = disease, outcome_var = "overall_rate_copd",horizon=horizon,significant_predictors = copd_discharge_significant_predictors)
        if (identical(combined_copd_df$actual, comparison_df$actual)) {
            final_df = cbind(combined_copd_df, comparison_df%>% dplyr::select(-actual))
        }
        
        combined_name_copd = paste0("admission_rate_", disease, horizon, "_", var, "_090325")
        assign(combined_name_copd, final_df)
        save_file_name = paste0(combined_name_copd, ".rdata")
        save(list = combined_name_copd, file = save_file_name)
      }
    }
  } else if (disease == "asthma"){
    for (var in vec){
      for (horizon in 1:12) {
        file_name = paste0("admission_rate_", disease, horizon, "_", var, "_050325.rdata")
        load(file_name)
        combined_asthma_df = submodels_asthma
        
        # Addition of Naive model
        comparison_df = addition_of_naive(df_link = "combined_asthma_env_080225_norates.csv", disease = disease, outcome_var = "overall_rate_asthma",horizon=horizon,significant_predictors = asthma_discharge_significant_predictors)
        if (identical(combined_asthma_df$actual, comparison_df$actual)) {
            final_df = cbind(combined_asthma_df, comparison_df%>% dplyr::select(-actual))
        }
        
        combined_name_asthma = paste0("admission_rate_", disease, horizon, "_", var, "_090325")
        assign(combined_name_asthma, final_df)
        save_file_name = paste0(combined_name_asthma, ".rdata")
        save(list = combined_name_asthma, file = save_file_name)
      }
    }
  }
  return("Done")
}

renaming_fn(variables, "copd")
renaming_fn(variables, "asthma")

# Part 2: Combination to a single dataframe
rm(list=ls())
file_name = paste0("admission_rate_asthma12_exog_090325.rdata")
load(file_name)
exog_initial_col_names = colnames(admission_rate_asthma12_exog_090325)
exog_temp_df = get(paste0("admission_rate_asthma12_exog_090325"))
exog_temp_df$index = seq_len(nrow(exog_temp_df))
exog_temp_df$horizon = 7
exog_col_names = colnames(exog_temp_df)
exog_len = length(exog_col_names)

for (disease in c("copd","asthma")){
  overall_df_combined = data.frame(matrix(ncol = exog_len, nrow = 0))
  colnames(overall_df_combined) = exog_col_names
  for (horizon in 1:12) {
    file_name = paste0("admission_rate_", disease, horizon, "_exog", "_090325.rdata")
    load(file_name)
    temp_df = get(paste0("admission_rate_", disease, horizon, "_exog", "_090325"))
    rownames(temp_df) = NULL
    colnames(temp_df) = exog_initial_col_names
    temp_df$index = seq_len(nrow(temp_df))
    temp_df$horizon = horizon
    overall_df_combined = rbind(overall_df_combined, temp_df)
  }
  overall_final_df = overall_df_combined %>%
    rename("aml_predictions" = "aml_prediction") %>%
    tidyr::fill(gam_lss_predictions, .direction = "down")
  combined_name_var = paste0(disease, "_exog", "_combined_090325")
  assign(combined_name_var, overall_final_df)
  save_file_name = paste0(combined_name_var, ".rdata")
  save(list = combined_name_var, file = save_file_name)
}

```

# Formation of dataframes for aggregated factors
- In this section, it details how to regenerate
- Based on the forecasted admission rates, multiply it by the corresponding residents population for aggregation, then compare against the true overall rate

```{r}
rm(list=ls())
gender_factors = c("female","male")
copd_age_factors = c("age_55_to_64", "age_65_to_74", "age_75_to_84","age_85_above")
asthma_age_factors = c("age_15_to_39", "age_40_to_54","age_55_to_64","age_65_to_74", "age_75_to_84", "age_85_above")

for (var in c(copd_age_factors,gender_factors)){
  file_name = paste0("copd_",var,"_all_280225.rdata")
  load(file_name)
}

for (var in c(asthma_age_factors,gender_factors)){
  file_name = paste0("asthma_",var,"_all_280225.rdata")
  load(file_name)
}

data_editing_subgroups = function(df_filename, outcome, significant_predictors){
  combined_df = read_csv(df_filename)%>%
    column_to_rownames(var = "...1")
  actual_outcome = sub("_([^_]+)$", "", outcome)
  last_part = sub(".*_(.*)$", "\\1", outcome)
  overall_rate = colnames(combined_df)[str_detect(colnames(combined_df), paste0(actual_outcome,"_residents","_",last_part))]
  new_combined = combined_df %>% 
    dplyr::select(overall_rate, significant_predictors)
  return(new_combined)
}

data_editing_subgroups_cases = function(df_filename, outcome, significant_predictors){
  combined_df = read_csv(df_filename)%>%
    column_to_rownames(var = "...1")
  new_combined = combined_df %>% 
    dplyr::select(outcome, significant_predictors)
  return(new_combined)
}

generate_lagged_df_subgroups = function(df, copd_lag_num, asthma_lag, env_lag, outcome){
  lagged_df = df
  lagged_cols_df = lagged_df %>%
      dplyr::select(outcome) 
  
  # Customisation of function based off the outcome (COPD / Asthma)
  if (str_detect(outcome, "copd")){
    other_disease = "asthma"
    outcome_lag = copd_lag_num
    other_disease_lag = asthma_lag
  } else if (str_detect(outcome, "asthma")){
    other_disease = "copd"
    outcome_lag = asthma_lag
    other_disease_lag = copd_lag_num
  }
  
  # Loop through all columns in the dataset
  for (col in colnames(df)){
    if (col == "year"|col == "week"){
      next
    } else if (col == outcome){
      for (i in 1:outcome_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := (lagged_col))
      }
    } else if (grepl(other_disease, col)){
      for (i in 1:other_disease_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := (lagged_col))
      }
    } else {
      for (i in 1:env_lag){
      lagged_col = dplyr::lag(df[[col]], i)
      lagged_cols_df = lagged_cols_df %>% 
        dplyr::mutate(!!paste0(col, "_L", i) := lagged_col)
      }
    }
  }
  lagged_df_final = na.omit(lagged_cols_df)
  return(lagged_df_final)
}

create_stepped_dataset = function(df, horizon, outcome) {
  shifted_df = df
  y = dplyr::lead(shifted_df[[outcome]], n = (horizon - 1))
  
  if (horizon != 1) {
    X = shifted_df[1:(nrow(shifted_df)-(horizon-1)),] # Removing the number of rows that y was shifted up
  } else {
    X = shifted_df
  }
  X = X %>% dplyr::select(-outcome) # Removing of outcome variable
  y = na.omit(y)
  
  return(list(X = X, y = y))
}

copd_significant_predictors_1 = c("overall_rate_asthma", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
asthma_significant_predictors_1 = c("overall_rate_copd", "MaxWind", "MeanWind", "MeanTemp", "MaxTemp", "MinTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")

# Extraction of residents column from the original dataframe
generate_residents_fn = function(df_link, outcome_var, copd_lag_num = 1, asthma_lag = 1, env_lag = 1, horizon, training_limit=0.5, significant_predictors, cases = F, dis){
  if (cases == T){
    outcome_var = paste0("residents_",dis)
    df = data_editing_subgroups_cases(df_link, outcome_var, significant_predictors = significant_predictors)
  } else{
    df = data_editing_subgroups(df_link, outcome_var, significant_predictors = significant_predictors)
  }
  
  env_variables_to_lag = c("MaxWind", "MeanWind", "MaxTemp", "MinTemp", "MeanTemp", "hot_week_indicator", "heat_wave_week", "Daily_Total_Rainfall")
  other_disease_var = setdiff(significant_predictors, 
                             c(outcome_var, env_variables_to_lag))
  
  training_length = floor(nrow(df)*training_limit) # Number of observations used for training the data
  initial_theta = 10
  actual_outcome = sub("_([^_]+)$", "", outcome_var)
  last_part = sub(".*_(.*)$", "\\1", outcome_var)
  if (cases == F){
    outcome_var = paste0(actual_outcome,"_residents","_",last_part)
  }
  
  filtered_df = df %>% 
    dplyr::select(outcome_var,all_of(significant_predictors))
  
  regression_model = generate_lagged_df_subgroups(filtered_df, copd_lag_num, asthma_lag, env_lag, outcome = outcome_var)
  X_1 = create_stepped_dataset(regression_model, horizon, outcome = outcome_var)[[1]]
  outcome_var_vec = create_stepped_dataset(regression_model, horizon, outcome = outcome_var)[[2]]
  stepped_df = cbind(X_1, outcome_var_vec) # Combination to form stepped df
  stepped_df = stepped_df %>% rename(!!outcome_var := "outcome_var_vec")
  n = nrow(stepped_df) # Length of stepped df
  stepped_df = stepped_df %>%
    mutate(across(everything(), ~ ifelse(is.infinite(.) & . < 0, 0, .)))
  
  test_set = stepped_df[(training_length + 1):n,]
  final_df = test_set %>%
    dplyr::select(dplyr::matches("residents") & dplyr::matches("L1"))
  return(final_df)
}

# Generation of full residents' df across all horizons
overall_residents_df = function(df_link, outcome_var, copd_lag_num = 1, asthma_lag = 1, env_lag = 1, horizon, training_limit=0.5, significant_predictors,cases=F, dis = "copd"){
  final_df = data.frame(matrix(ncol = 2, nrow = 0))
  sample_df = generate_residents_fn(df_link, outcome_var, copd_lag_num = 1, asthma_lag = 1, env_lag = 1, horizon = 1, training_limit=0.5, significant_predictors = significant_predictors, cases, dis)
  
  colnames(final_df) = c(colnames(sample_df),"horizon")
  for (horizon_num in 1:12){
    to_add = generate_residents_fn(df_link, outcome_var, copd_lag_num = 1, asthma_lag = 1, env_lag = 1, horizon = horizon_num, training_limit=0.5, significant_predictors = significant_predictors, cases, dis)
    to_add = to_add %>% mutate(horizon = horizon_num)
    final_df = rbind(final_df, to_add)
  }
  return(final_df)
}

# multiplying / dividing by the corresponding residents column to obtain for aggregation
combine_and_manipulate = function(residents_df, final_df, op = "multiply") {
  # Assuming 'residents_df' has a column called 'residents' and 'final_df' has prediction columns.
  final_df$residents = residents_df %>%
    dplyr::select(dplyr::contains("residents")) %>%
    pull()
  if (op == "multiply"){
    prediction_columns = c("actual", "naive_predictions", "ar_mixed_predictions", "gam_xgboost_predictions", "gam_lss_predictions", "glm_gamsel_predictions", "aml_predictions")
  } else {
    prediction_columns = c("actual", "naive_predictions", "ar_predictions", "gam_xgboost_predictions", "gam_lss_predictions", "glm_gamsel_predictions", "aml_predictions")
  }
  for (col in prediction_columns) {
    if (op == "multiply"){
      final_df[[col]] = final_df[[col]] * final_df$residents
    } else if (op == "divide") {
      final_df[[col]] = final_df[[col]] / final_df$residents
    }
  }
  # Remove the residents column after multiplication
  final_df = final_df %>% dplyr::select(-residents)
  return(final_df)
}

# Extraction of predictions from individually forecasted
ext_fn = function(disease, vec){
  filename = paste0(disease,"_",vec,"_all_280225")
  df = get(filename)
  final_df = df %>%
    dplyr::select(horizon, actual, naive_predictions, ar_mixed_predictions, gam_xgboost_predictions, gam_lss_predictions, glm_gamsel_predictions, aml_predictions)
  return(final_df)
}

# Age
for (dis in c("copd", "asthma")){
  if (dis == "copd"){
    first_var = copd_age_factors[1]
    var_name = paste0(first_var,"_",dis)
    residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = copd_significant_predictors_1)
    extracted_df = ext_fn(dis, first_var)
    copd_age_combined_050325 = combine_and_manipulate(residents_df, extracted_df)
    for (i in 2:length(copd_age_factors)){
      var_in_loop = copd_age_factors[i]
      var_name = paste0(var_in_loop,"_", dis)
      residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = copd_significant_predictors_1)
      df_to_add = ext_fn(dis, var_in_loop)
      df_to_add_new = combine_and_manipulate(residents_df, df_to_add)
      copd_age_combined_050325 = copd_age_combined_050325 + df_to_add_new
    }
    copd_age_combined_050325 = copd_age_combined_050325 %>% 
      mutate(horizon = horizon / length(copd_age_factors)) %>%
      rename("ar_predictions" = "ar_mixed_predictions")
    residents_overall = overall_residents_df("combined_asthma_env_080225_norates.csv", "", horizon, training_limit = 0.5, significant_predictors = copd_significant_predictors_1, cases = T, dis = "copd")
    copd_age_combined_090325 = combine_and_manipulate(residents_overall, copd_age_combined_050325, op = "divide")
  } else {
    first_var = asthma_age_factors[1]
    var_name = paste0(first_var,"_",dis)
    residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = asthma_significant_predictors_1)
    extracted_df = ext_fn(dis, first_var)
    asthma_age_combined_050325 = combine_and_manipulate(residents_df, extracted_df)
    for (i in 2:length(asthma_age_factors)){
      var_in_loop = asthma_age_factors[i]
      var_name = paste0(var_in_loop,"_", dis)
      residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = asthma_significant_predictors_1)
      df_to_add = ext_fn(dis, var_in_loop)
      df_to_add_new = combine_and_manipulate(residents_df, df_to_add)
      asthma_age_combined_050325 = asthma_age_combined_050325 + df_to_add_new
    }
    asthma_age_combined_050325 = asthma_age_combined_050325 %>% 
      mutate(horizon = horizon / length(asthma_age_factors)) %>%
      rename("ar_predictions" = "ar_mixed_predictions")
    residents_overall = overall_residents_df("combined_asthma_env_080225_norates.csv", "", horizon, training_limit = 0.5, significant_predictors = asthma_significant_predictors_1, cases = T, dis = "asthma")
    asthma_age_combined_090325 = combine_and_manipulate(residents_overall, asthma_age_combined_050325, op = "divide")
  }
}

for (dis in c("copd", "asthma")){
  if (dis == "copd"){
    first_var = gender_factors[1]
    var_name = paste0(first_var,"_",dis)
    residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = copd_significant_predictors_1)
    extracted_df = ext_fn(dis, first_var)
    copd_gender_combined_050325 = combine_and_manipulate(residents_df, extracted_df)
    for (i in 2:length(gender_factors)){
      var_in_loop = gender_factors[i]
      var_name = paste0(var_in_loop,"_", dis)
      residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = copd_significant_predictors_1)
      df_to_add = ext_fn(dis, var_in_loop)
      df_to_add_new = combine_and_manipulate(residents_df, df_to_add)
      copd_gender_combined_050325 = copd_gender_combined_050325 + df_to_add_new
    }
    copd_gender_combined_050325 = copd_gender_combined_050325 %>% 
      mutate(horizon = horizon / length(gender_factors)) %>%
      rename("ar_predictions" = "ar_mixed_predictions")
    residents_overall = overall_residents_df("combined_asthma_env_080225_norates.csv", "", horizon, training_limit = 0.5, significant_predictors = copd_significant_predictors_1, cases = T, dis = "copd")
    copd_gender_combined_090325 = combine_and_manipulate(residents_overall, copd_gender_combined_050325, op = "divide")
  } else {
    first_var = gender_factors[1]
    var_name = paste0(first_var,"_",dis)
    residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = asthma_significant_predictors_1)
    extracted_df = ext_fn(dis, first_var)
    asthma_gender_combined_050325 = combine_and_manipulate(residents_df, extracted_df)
    for (i in 2:length(gender_factors)){
      var_in_loop = gender_factors[i]
      var_name = paste0(var_in_loop,"_", dis)
      residents_df = overall_residents_df("combined_asthma_env_080225_norates.csv", var_name, horizon, training_limit = 0.5, significant_predictors = asthma_significant_predictors_1)
      df_to_add = ext_fn(dis, var_in_loop)
      df_to_add_new = combine_and_manipulate(residents_df, df_to_add)
      asthma_gender_combined_050325 = asthma_gender_combined_050325 + df_to_add_new
    }
    asthma_gender_combined_050325 = asthma_gender_combined_050325 %>% 
      mutate(horizon = horizon / length(gender_factors)) %>%
      rename("ar_predictions" = "ar_mixed_predictions")
    residents_overall = overall_residents_df("combined_asthma_env_080225_norates.csv", "", horizon, training_limit = 0.5, significant_predictors = asthma_significant_predictors_1, cases = T, dis = "asthma")
    asthma_gender_combined_090325 = combine_and_manipulate(residents_overall, asthma_gender_combined_050325, op = "divide")
  }
}

# save(asthma_age_combined_090325, file = "asthma_age_combined_090325_new.rdata")
# save(asthma_gender_combined_090325, file = "asthma_gender_combined_090325_new.rdata")
# save(copd_age_combined_090325, file = "copd_age_combined_090325_new.rdata")
# save(copd_gender_combined_090325, file = "copd_gender_combined_090325_new.rdata")
```

# Generation of Superensemble Models
- Method 1: Equal Weights
- Method 2: Median Weights
- Method 3: Bates and Granger --> Inverse SE
- Method 4: Bates and Granger --> Inverse Cumulative SE (Expanding Window)
- Method 5: Trimmed Mean

```{r}
rm(list=ls())
bates_granger_method_1 = function(df){
  model_names = colnames(df)

  # Filter names ending with "predictions" and remove the suffix
  new_names = model_names %>%
    str_subset("predictions$") %>%
    str_remove("_predictions")
  
  final_df = df %>%
    # group_by(horizon) %>%
    rowwise() %>%
    mutate(across(ends_with("predictions"), ~ (. - actual)^2, .names = "se_{str_remove(.col, '_predictions')}"),
           across(ends_with("predictions"), ~ 1/((. - actual)^2), .names = "inv_se_{str_remove(.col, '_predictions')}"),
           inv_se_sum = sum(c_across(starts_with("inv_se_")), na.rm = TRUE),
           across(starts_with("inv_se_"), ~ ./inv_se_sum, .names = "norm_{str_remove(.col, '_predictions')}"),
           across(starts_with("norm_"), ~if_else(is.nan(.), 1, .)))
  
  pred_col = paste0(new_names, "_predictions")
  norm_col = paste0("norm_inv_se_", new_names)
  pred_norm = final_df %>% dplyr::select(pred_col,norm_col,horizon)
  # return(pred_norm)
  final_weighted_preds = rowSums(map2_dfc(pred_col, norm_col, ~ {
    pred_norm[[.x]] * pred_norm[[.y]]
  }), na.rm = TRUE)
  
  return(final_weighted_preds)
}

bates_granger_method_2 = function(df){
  model_names = colnames(df)

  # Filter names ending with "predictions" and remove the suffix
  new_names = model_names %>%
    str_subset("predictions$") %>%
    str_remove("_predictions")
  
  final_df = df %>%
    rowwise() %>%
    mutate(across(ends_with("predictions"), ~ (. - actual)^2, .names = "se_{str_remove(.col, '_predictions')}")) %>%
    ungroup() %>%
    group_by(horizon) %>%
    mutate(across(starts_with("se"), cumsum, .names = "cumsum_{str_remove(.col, '_predictions')}")) %>%
    ungroup() %>%
    rowwise() %>%
    mutate(across(starts_with("cumsum_"), ~ 1/., .names = "inv_{str_remove(.col, '_predictions')}"),
           inv_se_sum = sum(c_across(starts_with("inv_cumsum_")), na.rm = TRUE),
           across(starts_with("inv_cumsum_se_"), ~ ./inv_se_sum, .names = "norm_{str_remove(.col, '_predictions')}"),
           across(starts_with("norm_"), ~if_else(is.nan(.), 1, .)))
  # return(final_df)
  pred_col = paste0(new_names, "_predictions")
  norm_col = paste0("norm_inv_cumsum_se_", new_names)
  pred_norm = final_df %>% dplyr::select(pred_col,norm_col)
  # return(pred_norm)
  final_weighted_preds = rowSums(map2_dfc(pred_col, norm_col, ~ {
    pred_norm[[.x]] * pred_norm[[.y]]
  }), na.rm = TRUE)
  return(final_weighted_preds)
}

superensem_generator = function(df){
  bg1_predictions = bates_granger_method_1(df)
  bg2_predictions = bates_granger_method_2(df)
  
  final_df = df %>%
    rowwise() %>%
    mutate(eq_weights_predictions = rowMeans(across(ends_with("predictions")), na.rm = TRUE),
           med_weights_predictions = median(c_across(ends_with("predictions")), na.rm = TRUE),
           trimmed_mean_predictions = mean(  c_across(ends_with("predictions")), 
      trim = 0.1,  # 10% trimmed mean
      na.rm = TRUE))
  final_df$bg1_predictions = bg1_predictions
  final_df$bg2_predictions = bg2_predictions
  return(final_df)
}

```

# Analysis 1
```{r}
# rm(list=ls())
final_var_1 = c("exog", "noexog")

for (dis in c("copd","asthma")){
  for (var in final_var_1){
    file_name = paste0(dis, "_", var, "_combined_090325.rdata")
    load(file_name)
    df = get(paste0(dis,"_", var, "_combined_090325"))
    final_df = superensem_generator(df)
    combined_name = paste0(dis,"_", var, "_combined_all_090325")
    assign(combined_name, final_df)
    save_file_name = paste0(combined_name, ".rdata")
    save(list = combined_name, file = save_file_name)
  }
}
```

# Analysis 2
```{r}
# final_var_2 = c("age_exog", "age", "gender_exog", "gender")
final_var_2 = c("age", "gender")

for (dis in c("copd","asthma")){
  for (var in final_var_2){
    file_name = paste0(dis, "_", var, "_combined_090325_new.rdata")
    load(file_name)
    df = get(paste0(dis,"_", var, "_combined_090325"))
    final_df = superensem_generator(df)
    combined_name = paste0(dis,"_", var, "_combined_all_090325")
    assign(combined_name, final_df)
    save_file_name = paste0(combined_name, ".rdata")
    save(list = combined_name, file = save_file_name)
  }
}
```