---
title: "05a plotting"
output: 
  pdf_document:
    dev: cairo_pdf
date: "2024-12-15"
---
# Description of File
In this coding file, the code to generate each graph will be shown for Analysis 1, which refers to the multi-step forecasting of COPD and asthma admission rates, and the subgroup admission rates for both diseases as well.

Therefore the file contains the following code:
(1) Code to generate plots in the paper
(2) Code to compare forecasting performances between models

# Loading the relevant packages
```{r setup, include=FALSE}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(lubridate)
library(cowplot)

asthma_variables = c("cases","female", "male", "age_15_to_39", "age_40_to_54", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")
copd_variables = c("cases", "female", "male", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")

for (var in copd_variables){
  file_name = paste0("copd_",var,"_all_280225.rdata")
  load(file_name)
}

for (var in asthma_variables){
  file_name = paste0("asthma_",var,"_all_280225.rdata")
  load(file_name)
}
```

## Plot 1: Explanation of Cases against Time 
- Main Text Figure 1
```{r}

var_df = function(df_link, var){
  df = read_csv(df_link)%>%
  column_to_rownames(var = "...1")
  colnames(df) = gsub(" \\(C\\)", "", colnames(df))
  colnames(df) = gsub(" \\(mm\\)", "", colnames(df))
  colnames(df) = gsub(" \\(kmh\\)", "", colnames(df))
  colnames(df) = gsub(" ", "_", colnames(df))
  final_df = df %>% dplyr::select(year, week, var)
  return(final_df)
}

asthma_df = var_df("combined_asthma_env_080225_norates.csv", "cases_asthma")
copd_df = var_df("combined_asthma_env_080225_norates.csv", "cases_copd")

plotter = function(df, disease, var){
  
  df$datetime = as.Date(paste0(df$year, "-W", sprintf("%02d", df$week), "-1"), format = "%Y-W%U-%u")
  shade_start = as.Date("2020-01-01")
  shade_end = as.Date("2022-12-31")
  
  start_date = min(df$datetime)
  midpoint_date = df$datetime[floor(nrow(df) / 2)]
  end_date = max(df$datetime)
  
  # Define shading data
  shading = data.frame(
    xmin = c(start_date, as.Date("2020-01-01")),
    xmax = c(as.Date("2020-01-01"), shade_end),
    ymin = -Inf,
    ymax = Inf,
    group = c("Training Set", "Structural Break")  # Add labels for the legend
  )
  
  shading_after_midpoint = data.frame(
    xmin = midpoint_date,
    xmax = max(df$datetime),
    ymin = -Inf,
    ymax = Inf,
    group = "Test Set"  # Add label for the legend
  )
  
  all_shading = rbind(shading, shading_after_midpoint)
  
  final_plot = ggplot(df, aes(x = datetime, y = !!sym(var))) +
    geom_rect(data = all_shading, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = group),
              alpha = 0.3, inherit.aes = FALSE) +
    geom_line(aes(color = "Observed"), size = 1) +  
    scale_y_continuous(limits = c(0, max(df[[var]]) + 13)) +
    scale_color_manual(
        values = c("Observed" = "black", "Raw Cases" = "maroon")
    ) +
    guides(fill = "none") +
    scale_fill_manual(values = c("Structural Break" = "red", "Test Set" = "lightgreen", "Training Set" = "lightblue")) +
    annotate("segment", x = start_date, xend = midpoint_date, 
             y = max(df[[var]]) + 6, yend = max(df[[var]]) + 6,
             arrow = arrow(length = unit(0.2, "cm"), ends = "both"), color = "black") +
    annotate("text", x = mean(c(start_date, midpoint_date)), 
             y = max(df[[var]]) + 7, 
             label = "Initial Training Set", hjust = 0.5, size = 10) +
    annotate("segment", x = midpoint_date, xend = as.Date("2023-12-31"), 
             y = max(df[[var]]) + 6, yend = max(df[[var]]) + 6,
             arrow = arrow(length = unit(0.2, "cm"), ends = "both"), color = "black") +
    annotate("text", x = mean(c(midpoint_date, as.Date("2023-12-31"))), 
             y = max(df[[var]]) + 7, 
             label = "Test Set 2 (With Structural Break)", hjust = 0.5, size = 10) +
    annotate("text", x = mean(c(shading$xmin[2], shade_end)), 
             y = max(df[[var]]) + 10, 
             label = "Structural Break", hjust = 0.5, size = 10, fontface = "bold") +
    annotate("segment", x = shading$xmin[2], xend = shade_end, 
             y = max(df[[var]]) + 9, yend = max(df[[var]]) + 9,
             arrow = arrow(length = unit(0.2, "cm"), ends = "both"), color = "black") +
    annotate("segment", x = shading_after_midpoint$xmin[1], xend = shading$xmin[2], 
             y = max(df[[var]]) + 2, yend = max(df[[var]]) + 2,
             arrow = arrow(length = unit(0.2, "cm"), ends = "both"), color = "black") +
    annotate("text", x = mean(c(shading_after_midpoint$xmin[1], shading$xmin[2])), 
             y = max(df[[var]]) + 4.25, 
             label = "Test Set 1", hjust = 0.5, size = 10) +
    annotate("text", x = mean(c(shading_after_midpoint$xmin[1], shading$xmin[2])), 
             y = max(df[[var]]) + 3, 
             label = "(No Structural Break)", hjust = 0.5, size = 10) +
    scale_x_date(date_breaks = "1 year", date_labels = "%Y", limits = as.Date(c("2012-01-01", "2023-12-31"))) +
    labs(
         x = "Year",
         y = "Cases",
         fill = "Period",
         color = NULL) +  # Remove title
    theme_minimal() +
    theme(
      axis.ticks = element_line(),  # Add axis ticks
      axis.ticks.length = unit(0.2, "cm"),
      plot.title = element_text(hjust = 0.5, size = 30),
      legend.position = c(0.1, 1),  # Top-left corner
      legend.justification = c(0, 1),
      panel.grid = element_blank(),
      # panel.background = element_rect(fill = "lightblue"),
      legend.box.background = element_rect(color = "black", fill = "white", size = 0.5),
      # legend.background = element_rect(fill = "white", color = NA),
      axis.title.y = element_text(face = "bold", size = 30),
      axis.title.x = element_text(face = "bold", size = 30),
      panel.border = element_rect(color = "black", fill = NA, size = 1),
      strip.text = element_text(size = 30),
      axis.text = element_text(size = 30),
      # legend.title = element_text(face = "bold", size=30),
      legend.text = element_text(size=30)
      
    )
  return(final_plot)
}
copd_admission = plotter(copd_df, "COPD", "cases_copd")
asthma_admission = plotter(asthma_df, "Asthma", "cases_asthma")
overall = plot_grid(
  copd_admission, asthma_admission,
  labels = "AUTO", ncol = 1, label_size = 50
)
ggsave(file="combined.pdf", plot=overall, width=20, height=25, limitsize=FALSE)
```

## Plot 2: PACF Plots
Main Text Figure 2: Plotting optimum PACF for each disease
- Same code as in 02 eda file
```{r}
combined_df = read_csv("combined_asthma_env_080225_norates.csv")%>%
  column_to_rownames(var = "...1")
colnames(combined_df) = gsub(" \\(C\\)", "", colnames(combined_df))
colnames(combined_df) = gsub(" \\(mm\\)", "", colnames(combined_df))
colnames(combined_df) = gsub(" \\(kmh\\)", "", colnames(combined_df))
colnames(combined_df) = gsub(" ", "_", colnames(combined_df))

combined_df_edited = combined_df

rownames_split = as.numeric(rownames(combined_df_edited)) 

years = floor(rownames_split / 100) 
weeks = rownames_split %% 100  

start_year = years[1]
start_week = weeks[1]

# Generating time series data
ts_data = ts(combined_df_edited$cases_copd, start = c(start_year, start_week), frequency = 52)
ts_data_asthma = ts(combined_df_edited$cases_asthma, start = c(start_year, start_week), frequency = 52)

pacf_plotter = function(df, var){
  pacf_values = acf(df[[var]], type = "partial", plot = FALSE)
  pacf_df = data.frame(
    Lag = as.vector(pacf_values$lag),
    PACF = as.vector(pacf_values$acf)
  )
  
  rownames_split = as.numeric(rownames(df))
  years = floor(rownames_split / 100) 
  weeks = rownames_split %% 100  
  
  start_year = years[1]
  start_week = weeks[1]
  
  ts_data = ts(df[[var]], start = c(start_year, start_week), frequency = 52)
  lag_val = 0
  for (lag_num in 1:20){
    lag_val = lag_val + 1
    pstat = Box.test(residuals(arima(ts_data,order=c(lag_num,0,0))), lag = 3, type = "Ljung-Box")$p.value
    # return(pstat)
    if (pstat > 0.01){
      final_pvalue = pstat
      break
    } else {
      next
    }
  }
  
  pacf_df = pacf_df %>% mutate(Shades = ifelse(Lag <= lag_val, "Used Lag", "Unused Lag"))
  
  final_plot = ggplot(pacf_df, aes(x = Lag, y = PACF, fill = Shades)) +
    geom_bar(stat = "identity") +
    labs(x = "Lags",
         y = "Partial Autocorrelation") +
    scale_y_continuous(limits=c(-0.1,0.5)) +
    theme_minimal() +
    theme(
      axis.ticks = element_line(),  # Add axis ticks
      axis.ticks.length = unit(1, "cm"),
      plot.title = element_text(hjust = 0.5, size = 30),
      legend.position = c(0.65, 1),  # Top-left corner
      legend.justification = c(0, 1),
      panel.grid = element_blank(),
      # panel.background = element_rect(fill = "lightblue"),
      legend.box.background = element_rect(color = "black", fill = "white", size = 0.5),
      # legend.background = element_rect(fill = "white", color = NA),
      axis.title.y = element_text(face = "bold", size = 50),
      axis.title.x = element_text(face = "bold", size = 50),
      panel.border = element_rect(color = "black", fill = NA, size = 1),
      strip.text = element_text(size = 50),
      axis.text = element_text(size = 50),
      legend.title = element_text(face = "bold", size=50),
      legend.text = element_text(size=50)
    )
  return(final_plot)
}

new_combined = combined_df_edited[1:floor(0.5*nrow(combined_df_edited)),]

x = pacf_plotter(new_combined, "cases_copd") + theme(legend.position = "none")+
  scale_y_continuous(breaks = waiver(),limits=c(-0.1,0.5)) +  # Add ticks on the y-axis
  theme(axis.text.x = element_blank(),     # Remove x-axis labels
        axis.ticks.x = element_blank()) + 
  labs(x = NULL)

legend = get_legend(
    pacf_plotter(new_combined, "cases_copd") +
      theme(legend.position = "right",
            legend.justification = c(0.3, 0.5),
            legend.box.margin = margin(0, 0, 0, -2),
            legend.title = element_text(size = 50, face = "bold"),
            legend.text = element_text(size = 45))
  )

y = pacf_plotter(new_combined, "cases_asthma")+ theme(legend.position = "none")

overall = plot_grid(plot_grid(x, y,labels = "AUTO", ncol = 1, label_size = 70,hjust = 0.05,vjust=1),
                            legend,
                            ncol = 2, 
                            rel_widths = c(6, 1))

ggsave(file="combined_pacf_280225.pdf", plot=overall, width=30, height=22.5, limitsize=FALSE)
```

## Plot 3: MAPE plotter
The code chunk below describes the generation of Main Text Figure 3 (COPD) and 4 (Asthma) which show the MAPE performance of forecasting models for raw admission cases and admission rates for subgroups for both diseases. 

It is to note that only MAPE is plotted. MAE and MASE will be included in data tables in Supplementary Information.

```{r}
mape_df_generator = function(df, structural_break){
  if (structural_break == T){
    df_long = df %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon)%>%
      filter(actual != 0) %>%
      summarise(mape = 100*mean(abs(actual - pred) / actual,na.rm=T),.groups="drop")
    return(df_long)
  } else {
    df_long = df %>%
      group_by(horizon) %>%
      slice_head(prop = 0.3) %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon)%>%
      filter(actual != 0) %>%
      summarise(mape = 100*mean(abs(actual - pred) / actual,na.rm=T),.groups="drop")
    return(df_long)
  }
}

model_group_num = c(
  "MLP" = "Unrestricted Models",
  "AR (C)" = "Simple Models",
  "AR (D)" = "Simple Models",
  "AR (B)" = "Simple Models",
  "BG1" = "Forecast Combinations",
  "BG2" = "Forecast Combinations",
  "SA" = "Forecast Combinations",
  "GAMLSS" = "Unrestricted Models",
  "GAM-XGBoost" = "Two-Step Forecasting Models",
  "GLM-GAMSEL" = "Two-Step Forecasting Models",
  "MF" = "Forecast Combinations",
  "Naive" = "Simple Models",
  "AR (A)" = "Simple Models",
  "TM" = "Forecast Combinations"
)

var_name_mapping = c(
  "age_0_to_14" = "Ages 0 to 14",
  "age_15_to_39" = "Ages 15 to 39",
  "age_40_to_54" = "Ages 40 to 54",
  "age_55_to_64" = "Ages 55 to 64",
  "age_65_to_74" = "Ages 65 to 74",
  "age_75_to_84" = "Ages 75 to 84",
  "age_85_above" = "85 and above",
  "cases" = "Admission Cases",
  "female" = "Female",
  "male" = "Male"
)

shapes_list = seq(5,19)
mape_plotter = function(df, structural_break = T, title_name, dis){
  
  if (structural_break == T){
    structural_break_bin = "With Structural Break"
  } else {
    structural_break_bin = "Without Structural Break"
  }
  df_long = mape_df_generator(df, structural_break)
  combined_plot_mape = df_long %>% mutate(model_grp = model_group_num[model])
  
  unique_groups = unique(combined_plot_mape$model)
  
  shape_mapping = setNames(shapes_list[seq_along(unique_groups)], unique_groups)
  
  final_plot = ggplot(combined_plot_mape, aes(x = horizon, y = mape, color = model_grp, shape = model)) +
    geom_line(size = 3) +
    geom_point(size = 15, stroke = 3) +
    labs(
      title = paste(title_name),
      x = "Horizon", y = paste0("MAPE (", dis,", %)"), color = "Model Type", shape = "Model") +
    scale_shape_manual(values = shape_mapping) +
    scale_x_continuous(breaks = 1:12, limits = c(1, 12)) +
    scale_y_continuous(breaks = seq(0,100,by = 20), limits = c(0, 100)) +
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 75, face = "bold"),
      legend.position = "right",
      panel.grid = element_blank(),
      # legend.box.background = element_rect(color = "black", size = 2),
      axis.title.y = element_text(face = "bold",size=75),
      axis.title.x = element_text(face="bold",size=75),
      panel.border = element_rect(color = "black", fill = NA, size = 1),
      legend.title = element_text(face = "bold", size = 75),
      legend.text = element_text(size=75),
      strip.text = element_text(size = 75),
      axis.text = element_text(size = 75),
      legend.key.size = unit(2, "lines")
      )
  return(final_plot)
}

combined_plotter = function(disease, disease_var){
  all_plots_sb = list()
  if (disease == "asthma"){
    cap_disease = "Asthma"
    bot_margin = 20
  } else{
    cap_disease = "COPD"
    bot_margin = 20
  }
  
  legend = get_legend(mape_plotter(asthma_age_15_to_39_all_280225, structural_break = T, title_name = "",dis=cap_disease))

  for (i in seq_along(disease_var)){
    var = disease_var[i]
    df = get(paste0(disease, "_", var, "_all_280225"))
    var_name = paste0("A", i, ": ", var_name_mapping[[var]])
    plot = mape_plotter(df, structural_break = T, title_name = var_name,dis=cap_disease) + theme(legend.position = "none")
    if (i %% 2 != 0) {
      if (i != 1){
        plot = plot + theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())
      }
    }
    if (i <= length(disease_var) - 2) {
      if (i != 1){
        plot = plot + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
      }
    }
    plot = plot + theme(plot.margin = margin(t = 50, r = 0, b = 0, l = 0))
    all_plots_sb[[var_name]] = plot
  }
  
  all_plots_nsb = list()
  for (i in seq_along(disease_var)){
    var = disease_var[i]
    df = get(paste0(disease, "_", var, "_all_280225"))
    var_name = paste0("B", i, ": ", var_name_mapping[[var]])
    plot = mape_plotter(df, structural_break = F, title_name = var_name,dis=cap_disease) + theme(legend.position = "none") + theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())
    
    if (i <= length(disease_var) - 2) {
      if (i != 1){
        plot = plot + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
      }
    }
    plot = plot + theme(plot.margin = margin(t = 50, r = 0, b = 0, l = 0))
    all_plots_nsb[[var_name]] = plot
  }
  
  all_plots_sb_admission = all_plots_sb[[1]]
  all_plots_sb_subgroups = all_plots_sb[-1]
  
  all_plots_nsb_admission = all_plots_nsb[[1]]
  all_plots_nsb_subgroups = all_plots_nsb[-1]
  
  dashed_line = ggplot() + 
    geom_segment(aes(x = 0, xend = 0, y = -5, yend = 5), 
                 linetype = "dashed", size = 10, color = "black") +
    theme_void() + 
    theme(plot.margin = margin(0, 0, 0, 0, "cm"))
  
  final_plot = plot_grid(
    plot_grid(plot_grid(all_plots_sb_admission, 
                        plot_grid(plotlist = all_plots_sb_subgroups, ncol = 2, rel_widths = c(1.1,1)),
                        nrow=2,
                        rel_heights = c(1,4)),
              dashed_line,
              plot_grid(all_plots_nsb_admission, 
                        plot_grid(plotlist = all_plots_nsb_subgroups, ncol = 2),
                        nrow=2,
                        rel_heights = c(1,4)),
              ncol = 3, rel_widths = c(1.05, 0.05, 1)),
    legend,
    ncol = 2, rel_widths = c(4.5, 1)
  )
  
  return(final_plot)
}

asthma_mape = combined_plotter("asthma", asthma_variables)
ggsave(file="asthma_mape.pdf", plot=asthma_mape, width=90, height=85, limitsize=FALSE)

copd_mape = combined_plotter("copd", copd_variables)
ggsave(file="copd_mape.pdf", plot=copd_mape, width=90, height=65, limitsize=FALSE)

```

# Part 2: Comparison of Models through computation of Wald's Test
- The chunk below describes the function to compare the statistical significance of the differences in performance between models by comparing the models pair by pair, for all possible combinations at 95% significance level.

```{r}

calculate_proportions = function(df, significance_level = 0.05,horizon_num,structural_break=T) {
  final_df = data.frame(matrix(ncol = 3, nrow = 0))
  colnames(final_df) = c("Model 1", "Model 2", "Outcome")
  if (structural_break == T){
    df_long = df %>%
        filter(horizon == horizon_num) %>%
        ungroup() %>%
        dplyr::select(actual, ends_with("predictions")) %>%
        mutate(time = row_number()) %>%
        pivot_longer(
          cols = -c(time,actual), 
          names_to = "model", 
          values_to = "pred") %>%
        mutate(model = recode(model,
                              "aml_predictions" = "MLP",
                              "ar_env_predictions" = "AR (C)",
                              "ar_mixed_predictions" = "AR (D)",
                              "ar_other_disease_predictions" = "AR (B)",
                              "bg1_predictions" = "BG1",
                              "bg2_predictions" = "BG2",
                              "eq_weights_predictions" = "SA",
                              "gam_lss_predictions" = "GAMLSS",
                              "gam_xgboost_predictions" = "GAM-XGBoost",
                              "glm_gamsel_predictions" = "GLM-GAMSEL",
                              "med_weights_predictions" = "MF",
                              "naive_predictions" = "Naive",
                              "pure_ar_predictions" = "AR (A)",
                              "trimmed_mean_predictions" = "TM"
                              )) %>%
        mutate(pred = ifelse(pred<0,0,pred),
               err = abs(pred-actual))
  } else {
    df_long = df %>%
        filter(horizon == horizon_num) %>%
        ungroup() %>%
        slice_head(prop = 0.3) %>%
        dplyr::select(actual, ends_with("predictions")) %>%
        mutate(time = row_number()) %>%
        pivot_longer(
          cols = -c(time,actual), 
          names_to = "model", 
          values_to = "pred") %>%
        mutate(model = recode(model,
                              "aml_predictions" = "MLP",
                              "ar_env_predictions" = "AR (C)",
                              "ar_mixed_predictions" = "AR (D)",
                              "ar_other_disease_predictions" = "AR (B)",
                              "bg1_predictions" = "BG1",
                              "bg2_predictions" = "BG2",
                              "eq_weights_predictions" = "SA",
                              "gam_lss_predictions" = "GAMLSS",
                              "gam_xgboost_predictions" = "GAM-XGBoost",
                              "glm_gamsel_predictions" = "GLM-GAMSEL",
                              "med_weights_predictions" = "MF",
                              "naive_predictions" = "Naive",
                              "pure_ar_predictions" = "AR (A)",
                              "trimmed_mean_predictions" = "TM"
                              )) %>%
        mutate(pred = ifelse(pred<0,0,pred),
               err = abs(pred-actual))
  }
  
  model_names = unique(df_long$model)
  model_names_sorted = sort(model_names)
  pairs_matrix = combn(model_names_sorted, 2, simplify = TRUE)
  
  # Initialize a vector to store counts of how many times each model performs better
  better_count = setNames(rep(0, length(model_names_sorted)), model_names_sorted)
  total_comparisons = setNames(rep(0, length(model_names_sorted)), model_names_sorted)
  
  # Loop over all pairs and compute Wald statistic
  for (i in 1:ncol(pairs_matrix)) {
    model1 = pairs_matrix[1, i]
    # return(model1)
    model2 = pairs_matrix[2, i]
    # return(model2)
    
    compute_wald_one_sided = function(errors1, errors2) {
      mean_diff = mean(errors1 - errors2)
      var_diff = var(errors1 - errors2) / length(errors1)
      wald_stat = (mean_diff^2) / var_diff
      return(as.numeric(wald_stat))
    }

    model1_err = df_long %>% 
      filter(model == model1) %>%
      pull(err)
    
    model2_err = df_long %>%
      filter(model == model2) %>%
      pull(err)
    # Compute Wald statistic
    wald_stat = compute_wald_one_sided(model1_err,model2_err)
    # Chi-squared critical value (df = 1 for one-sided comparison)
    critical_value = qchisq(1 - significance_level, df = 1)

    if (wald_stat > critical_value) { # Means there is statistically significant difference in forecast accuracy
      if (mean(model1_err) < mean(model2_err)){
        better_count[model1] = better_count[model1] + 1
        outcome = "Model 1"
        print(paste(model1, "is better than",model2))
      } else {
        better_count[model2] = better_count[model2] + 1
        outcome = "Model 2"
        print(paste(model1,  "is worse than",model2))
      }
    } else {
      better_count[model2] = better_count[model2] + 1
      outcome = "Equivalent"
      print(paste("Both", model1, "and", model2, "are equivalent"))
    }
    new_row = data.frame(`Model 1` = model1, 
                      `Model 2` = model2, 
                      Outcome = outcome)
    final_df = rbind(final_df, new_row)
    # Count the total number of comparisons for each model
    total_comparisons[model1] = total_comparisons[model1] + 1
    total_comparisons[model2] = total_comparisons[model2] + 1
  }
  
  # Calculate the proportion of times each model performs better
  proportion_better = better_count / total_comparisons
  return(final_df)
}

```


The chunk below describes the function to plot the statistical significance of the difference in forecasting performance of the models. There are the plots generated:

(1) Main Text Plot - This plot only contains 4 horizons for ease of reference in the paper

```{r}

relative_perf_plotter = function(df, horizon_num, structural_break = T, si = T){
  if (structural_break == T){
    struc_bin = "With Structural Break"
  } else {
    struc_bin = "Without Structural Break"
  }
  proportions_df = calculate_proportions(df,horizon_num = horizon_num, structural_break = structural_break)
  proportions_df$Model.1 = factor(proportions_df$Model.1, levels = unique(proportions_df$Model.1))
  proportions_df$Model.2 = factor(proportions_df$Model.2, levels = rev(unique(proportions_df$Model.2)))
  if (si == T){
    shape_size = 44
    text_size = 75
  } else {
    shape_size = 35
    text_size = 72
  }
  final_plot = ggplot() +
    geom_point(data = proportions_df, aes(x = Model.1, y = Model.2, color = Outcome, fill = Outcome, alpha = Outcome), shape = 22, size = shape_size) +
    theme_minimal() +
    scale_alpha_manual(values = c(0.2, 0.7, 0.7), 
                       labels = c("Equivalent", "Model 1", "Model 2")) +
    labs(title = paste("Comparison of Models", struc_bin),
         x = "Model 1",
         y = "Model 2",
         color = "Better Performing Model",
         fill = "Better Performing Model",
         alpha = "Better Performing Model") +
    theme(plot.title = element_text(hjust = 0.5, size = text_size),
          panel.grid = element_blank(),
          legend.position = c(1.1, 0.9), # Top-right position
          legend.justification = c("right", "top"),
          axis.title.y = element_text(face = "bold",size=text_size),
          axis.title.x = element_text(face="bold",size=text_size-5),
          legend.title = element_text(face = "bold", size = text_size),
          legend.text = element_text(size=text_size),
          strip.text = element_text(size = text_size),
          axis.text = element_text(size = text_size),
          axis.text.x = element_text(angle = 45, hjust = 1, size = text_size-3),
          legend.key.size = unit(2, "lines"),
          aspect.ratio = 2/2
          )
  return(final_plot)
}

letters_si = c("A","B","C","D","E","F","G","H","I","J","K","L")
letters_main_text = c("A","B","C","B","E","F","G","C","I","J","K","D")

plot_horizons_without_legend_maintext = function(df, horizons, structural_break = T, first_row = F, last_row = F, row_lab) {
  if (first_row == F && last_row == T){
    plots = lapply(horizons, function(h) {
      p = relative_perf_plotter(df, horizon_num = h, structural_break = structural_break, si = F) +
        labs(title = paste0(row_lab, which(horizons == h),": ", h,"-week(s) ahead")) +
        theme(
          plot.title = element_text(face = "bold", size = 80),
          # plot.title = element_blank(),
              legend.position = "none",
              axis.title.y = if (h == min(horizons)) element_text() else element_blank(),
              axis.text.y = if (h == min(horizons)) element_text() else element_blank(),
              axis.ticks.y = if (h == min(horizons)) element_line() else element_blank(),
              plot.margin = unit(c(0.5, -2, 0, -4), "cm"))
      return(p)
    })
  } else if (first_row == T && last_row == F){
    plots = lapply(horizons, function(h) {
      p = relative_perf_plotter(df, horizon_num = h, structural_break = structural_break, si = F) +
        labs(title = paste0(row_lab, which(horizons == h),": ", h,"-week(s) ahead")) +
        theme(
              plot.title = element_text(face = "bold", size = 80),
              legend.position = "none",
              axis.text.x = element_blank(),     # Remove x-axis labels
              axis.ticks.x = element_blank(),
              axis.title.y = if (h == min(horizons)) element_text() else element_blank(),
              axis.text.y = if (h == min(horizons)) element_text() else element_blank(),
              axis.ticks.y = if (h == min(horizons)) element_line() else element_blank(),
              plot.margin = unit(c(0.5, -2, 0, -4), "cm")) + 
  labs(x = NULL)
      return(p)
    })
  } else {
    plots = lapply(horizons, function(h) {
      p = relative_perf_plotter(df, horizon_num = h, structural_break = structural_break, si = F) +
        labs(title = paste0(row_lab, which(horizons == h),": ", h,"-week(s) ahead")) +
        theme(
          plot.title = element_text(face = "bold", size = 80),
              legend.position = "none",
              axis.text.x = element_blank(),     # Remove x-axis labels
              axis.ticks.x = element_blank(),
              axis.title.x = element_blank(),
              axis.title.y = if (h == min(horizons)) element_text() else element_blank(),
              axis.text.y = if (h == min(horizons)) element_text() else element_blank(),
              axis.ticks.y = if (h == min(horizons)) element_line() else element_blank(),
              plot.margin = unit(c(0.5, -2, 0, -4), "cm")
              )
      return(p)
    })
  }
  
  final_plot = plot_grid(plotlist = plots, 
                         # labels = plot_labels_new, 
                         label_size = 80, label_x = 0.15,
                         ncol = 4, nrow = 1, rel_widths = c(2,1.7,1.7,1.7))
  return(final_plot)
}

legend_extractor = function(df, horizons, structural_break = T, si = T) {
  if (si == T){
    legend_size = 90
  } else {
    legend_size = 95
  }
  # Extract the legend from the first plot
  legend = get_legend(
    relative_perf_plotter(df, horizon_num = horizons[1], structural_break = structural_break) +
      theme(legend.position = "right",
            legend.justification = c(0.3, 0.5),  # Adjust to keep it centered vertically
            legend.title = element_text(size = legend_size, face = "bold"),  # Adjust font size for legend title
            legend.text = element_text(size = legend_size),
            legend.box.background = element_rect(color = "black", size = 2),
            legend.direction = "horizontal") # Ensure the legend is positioned correctly
  )
  
  return(legend)
}

horizons_si = 1:12
horizons_main_text = c(1,4,8,12)

# Plotting of Main Text

copd_with_struc_break = plot_horizons_without_legend_maintext(copd_cases_all_280225, horizons_main_text, structural_break = T, first_row = T, row_lab = "A")
copd_without_struc_break = plot_horizons_without_legend_maintext(copd_cases_all_280225, horizons_main_text, structural_break = F, row_lab = "B")
asthma_with_struc_break = plot_horizons_without_legend_maintext(asthma_cases_all_280225, horizons_main_text, structural_break = T, row_lab = "C")
asthma_without_struc_break = plot_horizons_without_legend_maintext(asthma_cases_all_280225, horizons_main_text, structural_break = F, last_row = T, row_lab = "D")
legend = legend_extractor(asthma_cases_all_280225, horizons_main_text, structural_break = F)
maintext_plot = plot_grid(
  copd_with_struc_break,
  copd_without_struc_break,
  asthma_with_struc_break,
  asthma_without_struc_break,
  legend, nrow = 5,
  rel_heights = c(7,7,7,10.5,1)
)

ggsave(file="main_text_090325.pdf", plot=maintext_plot, width=90, height=65, limitsize=FALSE)

# plot_all_horizons_without_legend_new = function(df, horizons, structural_break = T) {
#   plots = lapply(horizons, function(h) {
#     p = relative_perf_plotter(df, horizon_num = h, structural_break = structural_break) +
#       labs(title = paste0(letters_si[h],": ", h,"-week(s) ahead")) +
#       theme(plot.title = element_text(face = "bold", size = 80),
#             legend.position = "none",
#             axis.text.y = if (h %in% c(1, 4, 7, 10)) element_text() else element_blank(),
#             axis.title.y = if (h %in% c(1, 4, 7, 10)) element_text() else element_blank(),
#             axis.text.x = if (h %in% c(10, 11, 12)) element_text() else element_blank(),
#             axis.title.x = if (h %in% c(10, 11, 12)) element_text() else element_blank(),
#             plot.margin = margin(50,0,0,0))
#     return(p)
#   })
#   final_plot = plot_grid(plotlist = plots, ncol = 3, nrow = 4, rel_widths = c(1.5,1,1), rel_heights = c(1,1,1,1.3))
#   return(final_plot)
# }
# 
# for (var in copd_variables){
#   df = get(paste0("copd_", var, "_all_100125"))
#   with_struc_break = plot_all_horizons_without_legend_new(df, horizons_si, structural_break = T)
#   without_struc_break = plot_all_horizons_without_legend_new(df, horizons_si, structural_break = F)
#   legend = legend_extractor(df, horizons_si, structural_break = F)
#   
#   file_name = paste0("copd_modelcomp_", var)
#   overall_struc_break = plot_grid(with_struc_break,
#     legend, nrow = 2,
#     rel_heights = c(20,1)
#   )
#   
#   overall_no_struc_break = plot_grid(without_struc_break,
#     legend, nrow = 2,
#     rel_heights = c(20,1)
#   )
#   
#   file_name = paste0("copd_", var, "_modelcomp_")
#   ggsave(file=paste0(file_name, "with_strucbreak_190125.pdf"), plot=overall_struc_break, width=65, height=90, limitsize=FALSE)
#   ggsave(file=paste0(file_name, "no_strucbreak_190125.pdf"), plot=overall_no_struc_break, width=65, height=90, limitsize=FALSE)
# }
# 
# for (var in asthma_variables){
#   df = get(paste0("asthma_", var, "_all_100125"))
#   with_struc_break = plot_all_horizons_without_legend_new(df, horizons_si, structural_break = T)
#   without_struc_break = plot_all_horizons_without_legend_new(df, horizons_si, structural_break = F)
#   legend = legend_extractor(df, horizons_si, structural_break = F)
#   
#   file_name = paste0("asthma_modelcomp_", var)
#   overall_struc_break = plot_grid(with_struc_break,
#                                   legend, nrow = 2,
#                                   rel_heights = c(20,1)
#   )
#   
#   overall_no_struc_break = plot_grid(without_struc_break,
#                                      legend, nrow = 2,
#                                      rel_heights = c(20,1)
#   )
#   
#   file_name = paste0("asthma_", var, "_modelcomp_")
#   ggsave(file=paste0(file_name, "with_strucbreak_190125.pdf"), plot=overall_struc_break, width=65, height=90, limitsize=FALSE)
#   ggsave(file=paste0(file_name, "no_strucbreak_190125.pdf"), plot=overall_no_struc_break, width=65, height=90, limitsize=FALSE)
# }
```
