---
title: "06a plotting"
output: 
  pdf_document:
    dev: cairo_pdf
date: "2024-12-15"
---
# Description of File

In this coding file, the code to generate each table in Supplementary Information S1 will be shown.

# Loading the relevant packages
```{r setup, include=FALSE}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(lubridate)
library(cowplot)

asthma_variables = c("cases","female", "male", "age_15_to_39", "age_40_to_54", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")
copd_variables = c("cases", "female", "male", "age_55_to_64", "age_65_to_74", "age_75_to_84", "age_85_above")
analysis_2_factors = c("age", "gender", "exog", "noexog")

for (var in copd_variables){
  file_name = paste0("copd_",var,"_all_280225.rdata")
  load(file_name)
}

for (var in asthma_variables){
  file_name = paste0("asthma_",var,"_all_280225.rdata")
  load(file_name)
}

for (var in analysis_2_factors){
  file_name = paste0("asthma_",var,"_combined_all_090325.rdata")
  load(file_name)
  file_name = paste0("copd_",var,"_combined_all_090325.rdata")
  load(file_name)
}
  file_name = paste0("copd_",var,"_combined_all_090325")
```

# General Functions
- data_editing, naive_model, and naive_mean_generator are used for computation for MASE

```{r}
data_editing = function(df_filename, outcome){
  combined_df = read_csv(df_filename)%>%
  column_to_rownames(var = "...1")
  
  if (outcome == "cases_copd"){
    popn = "residents_copd"
  } else if (outcome == "cases_asthma"){
    popn = "residents_asthma"
  } else {
    actual_outcome = sub("_([^_]+)$", "", outcome)
    last_part = sub(".*_(.*)$", "\\1", outcome)
    popn = colnames(combined_df)[str_detect(colnames(combined_df), paste0(actual_outcome,"_residents","_",last_part))]
  }
  new_combined = combined_df %>% 
    dplyr::select(year, week, outcome, popn)
  if (outcome == "male_asthma"|outcome=="male_copd"){
    new_combined = new_combined %>% 
      dplyr::select(-starts_with("female_residents"))
  }
  return(new_combined)
}

naive_model = function(df, horizon, outcome){
  df[[outcome]] = dplyr::lag(df[[outcome]],n=horizon)
  df = na.omit(df)
  return(df)
}

naive_mean_generator = function(df_link = "combined_asthma_env_080225_norates.csv", outcome_var, training_limit=0.5){
  df = data_editing(df_link, outcome_var)
  training_length = floor(nrow(df)*training_limit)
  naive_mae = function(df_use, horizon, outcome,training_len){
    naive_x = naive_model(df_use,horizon,outcome = outcome)[[outcome]]
    naive_y = df_use[(horizon+1):nrow(df_use),][[outcome_var]]
    naive_pred = naive_x[2:(training_len+1)]
    naive_actual = naive_y[2:(training_len+1)]
    mean_abs_err = mean(abs(naive_pred-naive_actual))
    return(mean_abs_err)
  }

  final_df = data.frame(horizon = numeric(), naive_mean = numeric(), stringsAsFactors = FALSE)
  for (horizon_num in 1:12){
    mae_horizon = naive_mae(df, horizon_num, outcome = outcome_var, training_len = training_length)
    to_add = data.frame(horizon = horizon_num, naive_mean = mae_horizon)
    final_df = rbind(final_df, to_add)
  }
  return(final_df)
}
```

# Generation Functions to compute error metrics for MAPE, MAE and MASE
- Each function has an argument of structural_break to determine if the evaluation period includes or excludes the structural break
```{r}
mape_df_generator = function(df, structural_break){
  if (structural_break == T){
    df_long = df %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon)%>%
      filter(actual != 0) %>%
      summarise(mape = 100*mean(abs(actual - pred) / actual,na.rm=T),.groups="drop")
    return(df_long)
  } else {
    df_long = df %>%
      group_by(horizon) %>%
      slice_head(prop = 0.3) %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon)%>%
      filter(actual != 0) %>%
      summarise(mape = 100*mean(abs(actual - pred) / actual,na.rm=T),.groups="drop")
    return(df_long)
  }
}

mae_df_generator = function(df, with_structural_break){
  if (with_structural_break == T){
    df_long = df %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(pred = ifelse(pred<0,0,pred)) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      summarise(mae = mean(abs(actual-pred)),.groups="drop")
    return(df_long)
    
  } else {
    df_long= df %>%
      group_by(horizon) %>%
      slice_head(prop = 0.3) %>%
      ungroup() %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(pred = ifelse(pred<0,0,pred)) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      summarise(mae = mean(abs(actual-pred)),.groups="drop")
    return(df_long)
  }
}

mase_df_generator = function(df, naive_mean_df, structural_break){
  if (structural_break == T){
    df_long = df %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      left_join(naive_mean_df, by="horizon") %>%
      summarise(mase = mean(abs(actual-pred))/naive_mean,.groups="drop") %>%
      unique()
    return(df_long)
  } else {
    df_long= df %>%
      group_by(horizon) %>%
      slice_head(prop = 0.3) %>%
      ungroup() %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_env_predictions" = "AR (C)",
                            "ar_mixed_predictions" = "AR (D)",
                            "ar_other_disease_predictions" = "AR (B)",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "med_weights_predictions" = "MF",
                            "naive_predictions" = "Naive",
                            "pure_ar_predictions" = "AR (A)",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      left_join(naive_mean_df, by="horizon") %>%
      summarise(mase = mean(abs(actual-pred))/naive_mean,.groups="drop") %>%
      unique()
    return(df_long)
  }
}
```

The chunk below describes the same functions, but for Analysis 2
```{r}
mape_df_generator_analysis2 = function(df, structural_break){
  if (structural_break == T){
    df_long = df %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_predictions" = "AR",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "med_weights_predictions" = "MF",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon)%>%
      filter(actual != 0) %>%
      summarise(mape = 100*mean(abs(actual - pred) / actual,na.rm=T),.groups="drop")
    return(df_long)
  } else {
    df_long = df %>%
      group_by(horizon) %>%
      slice_head(prop = 0.3) %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_predictions" = "AR",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "med_weights_predictions" = "MF",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon)%>%
      filter(actual != 0) %>%
      summarise(mape = 100*mean(abs(actual - pred) / actual,na.rm=T),.groups="drop")
    return(df_long)
  }
}

mae_df_generator_analysis2 = function(df, with_structural_break){
  if (with_structural_break == T){
    df_long = df %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(pred = ifelse(pred<0,0,pred)) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_predictions" = "AR",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "med_weights_predictions" = "MF",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      summarise(mae = mean(abs(actual-pred)),.groups="drop")
    return(df_long)
    
  } else {
    df_long= df %>%
      group_by(horizon) %>%
      slice_head(prop = 0.3) %>%
      ungroup() %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(pred = ifelse(pred<0,0,pred)) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_predictions" = "AR",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "med_weights_predictions" = "MF",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      summarise(mae = mean(abs(actual-pred)),.groups="drop")
    return(df_long)
  }
}

mase_df_generator_analysis2 = function(df, naive_mean_df, structural_break){
  if (structural_break == T){
    df_long = df %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_predictions" = "AR",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "med_weights_predictions" = "MF",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      left_join(naive_mean_df, by="horizon") %>%
      summarise(mase = mean(abs(actual-pred))/naive_mean,.groups="drop") %>%
      unique()
    return(df_long)
  } else {
    df_long= df %>%
      group_by(horizon) %>%
      slice_head(prop = 0.3) %>%
      ungroup() %>%
      dplyr::select(actual, horizon, ends_with("_predictions")) %>%
      pivot_longer(
        cols = -c(actual, horizon), 
        names_to = "model", 
        values_to = "pred"
      ) %>%
      mutate(model = recode(model,
                            "aml_predictions" = "MLP",
                            "ar_predictions" = "AR",
                            "gam_lss_predictions" = "GAMLSS",
                            "gam_xgboost_predictions" = "GAM-XGBoost",
                            "glm_gamsel_predictions" = "GLM-GAMSEL",
                            "bg1_predictions" = "BG1",
                            "bg2_predictions" = "BG2",
                            "eq_weights_predictions" = "SA",
                            "med_weights_predictions" = "MF",
                            "trimmed_mean_predictions" = "TM"
                            )) %>%
      group_by(model, horizon) %>%
      left_join(naive_mean_df, by="horizon") %>%
      summarise(mase = mean(abs(actual-pred))/naive_mean,.groups="drop") %>%
      unique()
    return(df_long)
  }
}
```

# Data: Supplementary Information S1 Data Tables

## PART 1: MAE CSV Generator

The code chunk below shows the functions involved in the generation of the data tables in S1
```{r}
mae_csv_generator = function(df, with_structural_break){
  err_metrics = mae_df_generator(df, with_structural_break) %>% 
      pivot_wider(
        names_from = model,   
        values_from = mae) %>% 
      mutate(across(where(is.numeric), ~ round(., 2)))
  if (with_structural_break == T){
    
    mean_values = df %>% 
      group_by(horizon) %>% 
      summarise(mean_case = signif(mean(actual),3),.groups="drop")
    final_df = err_metrics %>%
      inner_join(mean_values, by = "horizon")
  } else {
    mean_values = df %>% 
      group_by(horizon) %>% 
      slice_head(prop = 0.3) %>%
      summarise(mean_case = signif(mean(actual),3),.groups="drop")
    final_df = err_metrics %>%
      inner_join(mean_values, by = "horizon")
  }
  final_df = final_df %>% 
    dplyr::select(horizon,	Naive,	`AR (A)`,	`AR (B)`,	`AR (C)`,	`AR (D)`,	`GAM-XGBoost`,	`GAMLSS`,	`GLM-GAMSEL`, MLP,	BG1,	BG2,	SA,	MF, TM,	mean_case)
  return(final_df)
}

mae_csv_generator_2_analysis2 = function(df, with_structural_break){
  err_metrics = mae_df_generator_analysis2(df, with_structural_break) %>% 
      pivot_wider(
        names_from = model,   
        values_from = mae) %>% 
      mutate(across(where(is.numeric), ~ round(., 2)))
  if (with_structural_break == T){
    
    mean_values = df %>% 
      group_by(horizon) %>% 
      summarise(mean_case = signif(mean(actual),3),.groups="drop")
    final_df = err_metrics %>%
      inner_join(mean_values, by = "horizon")
  } else {
    mean_values = df %>% 
      group_by(horizon) %>% 
      slice_head(prop = 0.3) %>%
      summarise(mean_case = signif(mean(actual),3),.groups="drop")
    final_df = err_metrics %>%
      inner_join(mean_values, by = "horizon")
  }
  final_df = final_df %>% 
    dplyr::select(horizon, AR, GAMLSS, `GAM-XGBoost`, `GLM-GAMSEL`, MLP, BG1, BG2, SA, MF, TM, mean_case)
  return(final_df)
}

# Generation of Data Tables
mape_csv = function(df, structural_break){
  final = mape_df_generator(df, structural_break) %>% 
      pivot_wider(
        names_from = model,   
        values_from = mape) %>% 
      mutate(across(where(is.numeric), ~ round(., 2)))
  final = final %>% 
    dplyr::select(horizon,	Naive,	`AR (A)`,	`AR (B)`,	`AR (C)`,	`AR (D)`,	`GAM-XGBoost`,	`GAMLSS`,	`GLM-GAMSEL`, MLP,	BG1,	BG2,	SA,	MF, TM)
  return(final)
}

mape_csv_analysis2 = function(df, structural_break){
  final = mape_df_generator_analysis2(df, structural_break) %>% 
      pivot_wider(
        names_from = model,   
        values_from = mape) %>% 
      mutate(across(where(is.numeric), ~ round(., 2))) %>% 
      dplyr::select(horizon, AR, GAMLSS, `GAM-XGBoost`, `GLM-GAMSEL`, MLP, BG1, BG2, SA, MF, TM)
  return(final)
}

mase_csv = function(df, naive_mean_df, structural_break){
  final = mase_df_generator(df, naive_mean_df, structural_break) %>% 
      pivot_wider(
        names_from = model,   
        values_from = mase) %>% 
      mutate(across(where(is.numeric), ~ round(., 2)))
  final = final %>% 
    dplyr::select(horizon,	Naive,	`AR (A)`,	`AR (B)`,	`AR (C)`,	`AR (D)`,	`GAM-XGBoost`,	`GAMLSS`,	`GLM-GAMSEL`, MLP,	BG1,	BG2,	SA,	MF, TM)
  return(final)
}

mase_csv_analysis2 = function(df, naive_mean_df, structural_break){
  final = mase_df_generator_analysis2(df, naive_mean_df, structural_break) %>% 
      pivot_wider(
        names_from = model,   
        values_from = mase) %>% 
      mutate(across(where(is.numeric), ~ round(., 2))) %>% 
      dplyr::select(horizon, AR, GAMLSS, `GAM-XGBoost`, `GLM-GAMSEL`, MLP, BG1, BG2, SA, MF, TM)
  return(final)
}
```

Code chunk below describes the process of generation for all 3 metrics: MAE, MAPE and MASE

```{r}
##### METRIC 1: MAE #####
for (var in asthma_variables){
  file_name = paste0("asthma_",var,"_all_280225")
  file = get(file_name)
  df_struc = mae_csv_generator(file, with_structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("asthma_mae_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mae_csv_generator(file, with_structural_break = F)
  output_file_name = paste0("asthma_mae_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

for (var in copd_variables){
  file_name = paste0("copd_",var,"_all_280225")
  file = get(file_name)
  df_struc = mae_csv_generator(file, with_structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("copd_mae_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mae_csv_generator(file, with_structural_break = F)
  output_file_name = paste0("copd_mae_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

for (var in asthma_variables){
  file_name = paste0("asthma_",var,"_all_280225")
  file = get(file_name)
  df_struc = mae_csv_generator(file, with_structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("asthma_mae_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mae_csv_generator(file, with_structural_break = F)
  output_file_name = paste0("asthma_mae_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

# Data Tables for Analysis 2 (Exog vs Non-Exog, Aggregated vs Total)
for (var in analysis_2_factors){
  file_name = paste0("copd_",var,"_combined_all_090325")
  file = get(file_name)
  df_struc = mae_csv_generator_2_analysis2(file, with_structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("copd_mae_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mae_csv_generator_2_analysis2(file, with_structural_break = F)
  output_file_name = paste0("copd_mae_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

for (var in analysis_2_factors){
  file_name = paste0("asthma_",var,"_combined_all_090325")
  file = get(file_name)
  df_struc = mae_csv_generator_2_analysis2(file, with_structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("asthma_mae_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mae_csv_generator_2_analysis2(file, with_structural_break = F)
  output_file_name = paste0("asthma_mae_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

##### METRIC 2: MAPE CSV Code #####
for (var in asthma_variables){
  file_name = paste0("asthma_",var,"_all_280225")
  file = get(file_name)
  df_struc = mape_csv(file, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("asthma_mape_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mape_csv(file, structural_break = F)
  output_file_name = paste0("asthma_mape_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

for (var in copd_variables){
  file_name = paste0("copd_",var,"_all_280225")
  file = get(file_name)
  df_struc = mape_csv(file, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("copd_mape_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mape_csv(file, structural_break = F)
  output_file_name = paste0("copd_mape_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

# Data Tables for Analysis 2 (Exog vs Non-Exog, Aggregated vs Total)
for (var in analysis_2_factors){
  file_name = paste0("copd_",var,"_combined_all_090325")
  file = get(file_name)
  df_struc = mape_csv_analysis2(file, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("copd_mape_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mape_csv_analysis2(file, structural_break = F)
  output_file_name = paste0("copd_mape_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

for (var in analysis_2_factors){
  file_name = paste0("asthma_",var,"_combined_all_090325")
  file = get(file_name)
  df_struc = mape_csv_analysis2(file, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("asthma_mape_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mape_csv_analysis2(file, structural_break = F)
  output_file_name = paste0("asthma_mape_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

##### METRIC 3: MASE #####
for (var in copd_variables){
  file_name = paste0("copd_",var,"_all_280225")
  if (var == "discharge"){
    var_name = "cases"
  } else {
    var_name = var
  }
  outcome = paste0(var_name, "_copd")
  naive_mean_df = naive_mean_generator(outcome_var = outcome)
  file = get(file_name)
  df_struc = mase_csv(file, naive_mean_df, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("copd_mase_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mase_csv(file, naive_mean_df, structural_break = F)
  output_file_name = paste0("copd_mase_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

for (var in asthma_variables){
  file_name = paste0("asthma_",var,"_all_280225")
  if (var == "discharge"){
    var_name = "cases"
  } else {
    var_name = var
  }
  outcome = paste0(var_name, "_asthma")
  naive_mean_df = naive_mean_generator(outcome_var = outcome)
  file = get(file_name)
  df_struc = mase_csv(file, naive_mean_df, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("asthma_mase_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mase_csv(file, naive_mean_df, structural_break = F)
  output_file_name = paste0("asthma_mase_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}

# Data Tables for Analysis 2 (Exog vs Non-Exog, Aggregated vs Total)
for (var in analysis_2_factors){
  file_name = paste0("copd_",var,"_combined_all_090325")
  naive_mean_df = naive_mean_generator(outcome_var = "overall_rate_copd")
  file = get(file_name)
  df_struc = mase_csv_analysis2(file, naive_mean_df, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("copd_mase_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mase_csv_analysis2(file, naive_mean_df, structural_break = F)
  output_file_name = paste0("copd_mase_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}


for (var in analysis_2_factors){
  file_name = paste0("asthma_",var,"_combined_all_090325")
  naive_mean_df = naive_mean_generator(outcome_var = "overall_rate_asthma")
  file = get(file_name)
  df_struc = mase_csv_analysis2(file, naive_mean_df, structural_break = T)
  folder_name = paste0(var,"_err")
  if (!dir.exists(folder_name)) {
    dir.create(folder_name)
  }
  save_path = file.path(getwd(), folder_name)
  output_file_name = paste0("asthma_mase_", var, "_processed_with_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_struc, file = full_save_path, row.names = FALSE)
  
  df_no_struc = mase_csv_analysis2(file, naive_mean_df, structural_break = F)
  output_file_name = paste0("asthma_mase_", var, "_processed_no_structuralbreak.csv")
  full_save_path = file.path(save_path, output_file_name)
  write.csv(df_no_struc, file = full_save_path, row.names = FALSE)
}
```